---
title: Undecided
engine: knitr
format: gfm
bibliography: 
csl: apa.csl
from: markdown+wikilinks_title_after_pipe
link-citations: true
link-bibliography: true
---

[[Landscape/@Noppeney_2021/@Noppeney_2021|Multisensory processing]] occurs via integration across sensory modalities. But like any other system, our sensory apparatus adds noise to the incoming information. How are we able to perceive things so smoothly despite the uncertainty in the information received? Bayesian inference has been pegged as one of the possible mechanisms our brain uses to solve this intractable problem [@Noppeney_2021; @Kording_2007]. In addition to the noise generated by the sensory apparatus, the brain's computational resources are biologically constrained. Bayesian inference allows the internal processes in the brain to weigh the sensory information based on its reliability. Reliabilities provide a link between the internal model of the world and reality. Thus the weights are capturing the relationships which occur in the real world ie. the causal structure of the world around us. Integration of suboptimal information coming from different senses shows characteristics of normative (rule-based) bayesian framework [@Noppeney_2021]. One way to study this integration across modalities is to ask how does the brain differentiate if the information received is coming from common or independent sources ie. *the binding problem*. Spatial cognition is a prime example of the binding problem, especially in a naturalistic environment.
My main goal is to apply and confirm the mechanisms described in a multisensory integration review paper [@Noppeney_2021] to heading estimation task performed in VR [@Harootonian_2022].

## Experiment Design

33 participants wore VR headsets with controllers held in both hands in a rectangular room. Each participant performed ~400 trials for ~90 minutes. The sessions were divided into two blocks separated by a 2-10 minute break. The data from 3 participants is not present in the public dataset. These were excluded by the experimenters due to motion sickness or not enough recorded trials.  

### Trial and Block Structure

Each trial followed the following structure:

- **Encoding period**: Participant faces a door on the VR screen. They rotate around the vertical axis towards the controller which vibrates in the right or left hand. The stop of the vibrations signals the participant has arrived to a *target* angular rotation.
- **Retrieval period**: The VR screen goes blank and the participant is asked to rotate back to re-face the door. The direction choice for turning back was left to the participants. There were two types of retrieval periods:
    - *noFb* trials: No visual feedback is provided
    - *FB* trials: ~ 300 msec flash of the virtual environment is provided as feedback while they are turning back to re-face the door
- **Response period**: Participants press a button on the controller to record their response. No time limits were set.
- **Subjective rating period**: Paticipants adjust a red triangle's angle to indicate their confidence.

Each of the two blocks were divided into:

- **Practice period**: 10 trials
- **No Feedback period**: 25 trials
- **Feedback period**: 150 trials
- **No Feedback period**: 25 trials

### Ethological significance

The trial structure reminded me of when I would enter a room, grab something and leave through the door all the while focusing on my phone. Humans are able to perform this simple task with great fidelity even in novel environments. The immersive nature of the VR, free-choice for direction during the retrieval period and no time limits add to the ethological relevance of the experiment. The subjective rating period provides a reset time for the participants and may reduce the effects due to learning. Can adding a response action of opening the door in the virtual environment increase the ethological relevance?  

## Data Structure

```{r}
#| label: imports
#| code-summary: Imports
#| code-fold: true
# Import necessary libraries
library(here)
library(tidyverse)
library(tidymodels)
```

```{r}
#| label: download-data
#| code-summary: Download data
#| code-fold: true
# Get the data path
data_path <- here("data", "heading-estimation-multisensory-proc")
# Make the directory if it does not exist already
dir.create(data_path, recursive = TRUE, showWarnings = FALSE)
# Download dataconf.csv to data_path if not already present
if (!file.exists(file.path(data_path, "dataconf.csv"))) {
  dataconf_url <- "https://raw.githubusercontent.com/sharootonian/CombinationAndCompetitionHeadingDirection/main/data/dataconf.csv"
  download.file(dataconf_url, file.path(data_path, "dataconf.csv"), mode = "wb")
}
```

```{r}
#| label: preprocess-data
#| code-summary: Load, preprocess and split data into train, validation and test splits
#| code-fold: true

# Load data
dataconf <- read_csv(file.path(data_path, "dataconf.csv"))

# Prepare the data for train, validation and test splits
data <- dataconf %>%
  # Convert the subject column into a factor
  mutate(subj = factor(as.integer(str_remove(subj, "^s")))) %>%
  # Convert the condition column into a factor
  mutate(condition = factor(condition, levels = c("noFB", "FB"))) %>%
  # Since feedback validity labels are not present, use label reliable for gaussian (0, 30) +/- 3SD
  mutate(fb_validity = factor(case_when(condition == "noFB" ~ NA,
                                        abs(fb_offset) <= 90 ~ "reliable",
                                        TRUE ~ "unreliable"),
                              levels = c("reliable", "unreliable"))) %>%
  # Create a new column to signify the three trial types
  mutate(trial_type = if_else(condition == "noFB", "noFB", as.character(fb_validity))) %>%
  mutate(trial_type = factor(trial_type, levels = c("noFB", "reliable", "unreliable")))

# Split into train (80%), validation (10%) and test (10%) stratified by subj
set.seed(246) # For reproducibility
data_split <- initial_validation_split(data, prop = c(0.8, 0.1), strata = subj)
train <- training(data_split)
validation <- validation(data_split)
test <- testing(data_split)
```

`dataconf.csv` contains the following columns:

- *subj*: Participant identifier; `r length(unique(data$subj))` participants in total
- *trial*: Trial identifier
- *target* (degrees): Angle value where the controller vibration stops ranging from `0` to `360`; circularly uniform and anchored to the door
- *respond* (degrees): Total angle the participant turns ie. accumulates before the response
- *error* (degrees): `respond` - `target`; objective measure of performance
- *condition*: Marks `FB` vs. `noFB` trials
- *fb* (degrees): Angular position of the feedback shown; anchored to the door
- *fb_true* (degrees): True angular position of the feedback; anchored to the door
- *fb_offset* (degrees): `fb` - `fb_true`; signifies the reliability of the visual feedback. These were generated in two ways:
    - 70% of the trials: $\sim Gaussian(0, 30)$
    - 30% of the trials: $\sim Uniform(-180, 180)$
- *fb_time* (msec): Marks the time from trial start to feedback flash
- *trial_duration* (msec): Total time taken by the participant to press the response button from trial start
- *conf* (degrees): Response confidence level; subjective measure of performance
- *viewAmount* (degrees): View angle traversed by the participant while the visual feedback was visible; signifies how much attention was payed to the feedback. For eg., a lower `viewAmount` would suggest that the participant slowed down to reorient themselves to the new context obtained from the feedback

## Analysis (think of a descriptive title)

