---
title: Undecided
engine: knitr
# format: gfm
from: markdown+wikilinks_title_after_pipe
link-citations: true
link-bibliography: true
execute:
  cache: true
---

[[Landscape/@Noppeney_2021/@Noppeney_2021|Multisensory processing]] occurs via integration across sensory modalities. But like any other system, our sensory apparatus adds noise to the incoming information. How are we able to perceive things so smoothly despite the uncertainty in the information received? Bayesian inference has been pegged as one of the possible mechanisms our brain uses to solve this intractable problem [@Noppeney_2021; @Kording_2007]. In addition to the noise generated by the sensory apparatus, the brain's computational resources are biologically constrained. Bayesian inference allows the internal processes in the brain to weigh the sensory information based on its reliability. Reliabilities provide a link between the internal model of the world and reality. Thus the weights are capturing the relationships which occur in the real world ie. the causal structure of the world around us. Integration of suboptimal information coming from different senses shows characteristics of normative (rule-based) bayesian framework [@Noppeney_2021]. One way to study this integration across modalities is to ask how does the brain differentiate if the information received is coming from common or independent sources ie. *the binding problem*. Spatial cognition is a prime example of the binding problem, especially in a naturalistic environment.
My main goal is to apply and confirm the mechanisms described in a multisensory integration review paper [@Noppeney_2021] to heading estimation task performed in VR [@Harootonian_2022].

## Experiment Design

33 participants wore VR headsets with controllers held in both hands in a rectangular room. Each participant performed ~400 trials for ~90 minutes. The sessions were divided into two blocks separated by a 2-10 minute break. The data from 3 participants is not present in the public dataset. These were excluded by the experimenters due to motion sickness.  

### Trial and Block Structure

Each trial followed the following structure:

- **Encoding period**: Participant faces a door on the VR screen. They rotate around the vertical axis towards the controller which vibrates in the right or left hand. The stop of the vibrations signals the participant has arrived to a *target* angular rotation.
- **Retrieval period**: The VR screen goes blank and the participant is asked to rotate back to re-face the door. The direction choice for turning back was left to the participants. There were two types of retrieval periods:
    - *noFb* trials: No visual feedback is provided
    - *FB* trials: ~ 300 msec flash of the virtual environment is provided as feedback while they are turning back to re-face the door
- **Response period**: Participants press a button on the controller to record their response. No time limits were set.
- **Subjective rating period**: Paticipants adjust a red triangle's angle to indicate their confidence.

Each of the two blocks were divided into:

- **Practice period**: 10 trials
- **No Feedback period**: 25 trials
- **Feedback period**: 150 trials
- **No Feedback period**: 25 trials

### Ethological significance

The trial structure reminded me of when I would enter a room, grab something and leave through the door all the while focusing on my phone. Humans are able to perform this simple task with great fidelity even in novel environments. The immersive nature of the VR, free-choice for direction during the retrieval period and no time limits add to the ethological relevance of the experiment. The subjective rating period provides a reset time for the participants and may reduce the effects due to learning. Can adding a response action of opening the door in the virtual environment increase the ethological relevance?  

## Data Structure

```{r}
#| label: imports
#| code-summary: Imports
#| code-fold: true
#| message: false
# Import necessary libraries
library(here)
library(tidyverse)
library(tidymodels)
library(circular)
library(gridExtra)
library(boot)
library(quantreg)
library(rmcorr)
library(gamlss)
library(car)

# Pin the here() root explicitly
here::i_am("scripts/heading-estimation-multisensory-proc.qmd")
```

```{r}
#| label: download-data
#| code-summary: Download data
#| code-fold: true
# Get the data path
data_path <- here("data")
# Make the directory if it does not exist already
dir.create(data_path, recursive = TRUE, showWarnings = FALSE)
# Download dataconf.csv to data_path if not already present
if (!file.exists(file.path(data_path, "dataconf.csv"))) {
  dataconf_url <- "https://raw.githubusercontent.com/sharootonian/CombinationAndCompetitionHeadingDirection/main/data/dataconf.csv"
  download.file(dataconf_url, file.path(data_path, "dataconf.csv"), mode = "wb")
}
```

```{r}
#| label: preprocess-data
#| code-summary: Load, preprocess and split data into train and test splits
#| code-fold: true
#| message: false

# Load data
dataconf <- read_csv(file.path(data_path, "dataconf.csv"))

# Prepare the data for train and test splits
data <- dataconf %>%
  # Convert the subject column into a factor
  mutate(subj = factor(as.integer(str_remove(subj, "^s")))) %>%
  # Convert the condition column into a factor
  mutate(condition = factor(condition, levels = c("noFB", "FB")))

# Split into train (80%) and test (20%) by whole subjects
set.seed(246) # For reproducibility
data_split <- group_initial_split(data, group = subj, prop = 0.8)
train <- training(data_split)
test <- testing(data_split)
```

`dataconf.csv` contains the following columns:

- *subj*: Participant identifier; `r length(unique(data$subj))` participants in total
- *trial*: Trial identifier; some trials were excluded from the data when the participant rotated in the wrong direction during encoding period, pressed the wrong response button or responded before receiving the visual feedback
- *target* (degrees): Angle value where the controller vibration stops ranging from `0` to `360`; circularly uniform and anchored to the door
- *respond* (degrees): Total angle the participant turns during the retrieval period ie. accumulates before the response
- *error* (degrees): `respond` - `target`; objective measure of performance
- *condition*: Marks `FB` vs. `noFB` trials
- *fb* (degrees): Angular position of the feedback shown; anchored to the door
- *fb_true* (degrees): True angular position of the feedback; anchored to the door
- *fb_offset* (degrees): `fb` - `fb_true`; signifies the reliability of the visual feedback. These were generated in two ways:
    - 70% of the trials: $\sim Gaussian(0, 30)$
    - 30% of the trials: $\sim Uniform(-180, 180)$
- *fb_time* (msec): Marks the time from trial start to feedback flash
- *trial_duration* (msec): Total time taken by the participant to press the response button from trial start
- *conf* (degrees): Response confidence level; subjective measure of performance
- *viewAmount* (degrees): View angle traversed by the participant while the visual feedback was visible; signifies how much attention was payed to the feedback. For eg., a lower `viewAmount` would suggest that the participant slowed down to reorient themselves to the new context obtained from the feedback

## Analysis (think of a descriptive title)

### Stimulus Design

```{r}
#| label: fig-stimulus-design
#| fig-cap: "**Distributions of target heading and visual feedback offset across participants**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Confirm almost similar concentration of target angles is present across each subject
rho_by_subj <- train %>%
  summarise(rho = rho.circular(circular(target, units = "degrees")), .by = subj)
# Find the mean and sd of the concentration of target angles
rho_mean <- mean(rho_by_subj$rho)
rho_sd <- sd(rho_by_subj$rho)

# Define the 20 degree target bins for plotting purposes
target_bin_breaks <- seq(0, 360, by = 20)
target_bin_labels <- paste(head(target_bin_breaks, -1), tail(target_bin_breaks, -1), sep = "-")
target_bins <- cut(
  train$target, breaks = target_bin_breaks,
  include.lowest = TRUE, labels = target_bin_labels
)

# Show every 3rd bin label for even, uncluttered spacing
target_bin_ticks <- target_bin_labels[seq(1, length(target_bin_labels), by = 3)]

# Display distribution of target headings
plot_target <- train %>%
  # Divide target into 20 degree bins, dropping subj levels absent from train
  mutate(target_bin = target_bins, subj = factor(subj)) %>%
  count(subj, target_bin, .drop = FALSE) %>%
  # Summarize by subjects to confirm consistency
  group_by(subj) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  summarise(mean_prop = mean(prop), sd_prop = sd(prop), .by = target_bin) %>%
  ggplot(aes(x = target_bin, y = mean_prop)) +
  geom_col(colour = "steelblue", fill = "steelblue") +
  geom_errorbar(
    aes(ymin = mean_prop - sd_prop, ymax = mean_prop + sd_prop),
    width = 0.2
  ) +
  # Change to a circular coordinate
  coord_polar(start = 0) +
  labs(
    x = expression(paste("target heading (", degree, ")")),
    y = "proportion of trials"
  ) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 9)
  )

# Display distribution of fb_offset which was drawn from two components
breaks <- seq(-180, 180, by = 20)
bin_width <- 20
centers <- breaks[-length(breaks)] + bin_width / 2

fb_agg <- train %>%
  filter(condition == "FB") %>%
  mutate(
    bin_center = centers[cut(fb_offset, breaks = breaks, include.lowest = TRUE, labels = FALSE)],
    subj = factor(subj)
  ) %>%
  count(subj, bin_center, .drop = FALSE) %>%
  # Summarize by subjects to confirm consistency
  group_by(subj) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  summarise(mean_prop = mean(prop), se_prop = sd(prop) / sqrt(n()), .by = bin_center)

# Source distributions
theo_gaussian <- function(x) 0.7 * dnorm(x, 0, 30) * bin_width
theo_uniform  <- function(x) 0.3 * dunif(x, -180, 180) * bin_width

# Build the plot
plot_fb_offset <- ggplot(fb_agg, aes(x = bin_center, y = mean_prop)) +
  geom_col(width = bin_width * 0.9, fill = "grey70") +
  geom_errorbar(aes(ymin = mean_prop - se_prop, ymax = mean_prop + se_prop), width = bin_width * 0.2) +
  geom_function(aes(color = "~ Gaussian(0, 30)"), fun = theo_gaussian, xlim = c(-180, 180), linewidth = 1) +
  geom_function(aes(color = "~ Uniform(-180, 180)"), fun = theo_uniform, xlim = c(-180, 180), linewidth = 1) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Visual feedback offset", y = "proportion of FB trials", color = NULL) +
  theme_classic() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.position = "inside", legend.position.inside = c(1, 1),
    legend.justification = c(1, 1),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1.2, "lines")
  )

plot_target
plot_fb_offset
```

- Target headings are widely spread for all subjects (circular $\rho$ = `r round(rho_mean, 2)` $\pm$ `r 2*round(rho_sd, 2)`) (@fig-stimulus-design-1). The most likely explanation for this design decision might be to prevent formation of any pattern matching habits in the participants.
- Visual feedback offset distribution resembles a gaussian in the range of $0^\circ \pm 3 \times 30^\circ$ and uniform beyond that (@fig-stimulus-design-2), consistent with how the offsets were generated.

### Response Characteristics

```{r}
#| label: fig-respond-error-by-target
#| fig-cap: "**Mean respond and median error across target heading bins**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Define the number of bootstraps
R_boot <- 1000

# Compute the mean of respond per target bins
respond_boot_by_bin <- train %>%
  mutate(target_bin = target_bins, include.lowest = TRUE) %>%
  group_by(target_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      mean(samp$respond)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(mean = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for respond vs. target
plot_A <- ggplot(respond_boot_by_bin, aes(x = target_bin, y = mean)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "Mean(respond) with 95% bootstrap CI")

# Compute the median of error per target bins
error_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error vs. target
plot_B <- ggplot(error_boot_by_bin, aes(x = target_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "Median(error) with 95% bootstrap CI")

plot_A
plot_B

# Is error truly positively biased?
error_wilcox <- wilcox.test(train$error, mu = 0)
subjs <- unique(train$subj)
median_error_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  median(samp$error)
}, R = R_boot)
median_error_ci <- boot.ci(median_error_boot, type = "perc")$percent[4:5]

# Does error stay constant (flat trend) across target?
# Controlling for individual subjects
error_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(error ~ target, tau = 0.5, data = samp))["target"]
}, R = R_boot)
error_slope_ci <- boot.ci(error_slope_boot, type = "perc")$percent[4:5]

# Is respond's variance coming directly from error rather than target?
# ie. check if the last term in Var(respond) = var(target) + var(error) + 2 cov(target, error) -> 0
# Repeated measures correlation controls for subject to avoid pooling across subjects
respond_error_rmcorr <- rmcorr(subj, target, error, dataset = train)
```

- Respond angle increases monotonically with target, consistent with `respond` = `target` + `error` relationship (@fig-respond-error-by-target-1). The width of the bootstrapped (`1000`) 95% confidence interval (CI) also increases with target angle suggesting an increase in uncertainity with increasing difficulty of the task.
- Median error is consistently positive (Wilcoxon signed-rank test, `r ifelse(error_wilcox$p.value < 0.001, "p < 0.001", paste("p =", round(error_wilcox$p.value, 3)))`; bootstrapped median 95% CI [`r round(median_error_ci[1], 2)`, `r round(median_error_ci[2], 2)`]) but does not increase or decrease as a function of target angle (bootstrapped median regression slope 95% CI [`r round(error_slope_ci[1], 3)`, `r round(error_slope_ci[2], 3)`]). However, the width of the bootstrapped (`1000`) 95% CI for mean error increases with target angle just like respond (@fig-respond-error-by-target-2).
- The growing uncertainty in `respond` tracks `error` directly, since:

$$
\begin{aligned}
&respond = target + error \\
\implies &Var(respond) = Var(target) + Var(error) + 2\;Cov(target, error)
\end{aligned}
$$

  The repeated measures correlation between `target` and `error` is negligible ($r$ = `r round(respond_error_rmcorr$r, 3)`, 95% CI [`r round(respond_error_rmcorr$CI[1], 3)`, `r round(respond_error_rmcorr$CI[2], 3)`]). Thus, `error` can be used as the predicting variable instead of `respond` to model participant's response.

```{r}
#| label: fig-error-by-condition-offset
#| fig-cap: "**Median error by condition and by visual feedback offset magnitude**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Compute the median error per condition
condition_median_boot <- train %>%
  group_by(condition) %>%
  group_modify(~ {
    group_data <- .x
    group_subjs <- unique(group_data$subj)
    b <- boot(group_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ group_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error vs. condition
plot_C <- ggplot(condition_median_boot, aes(x = condition, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(labels = c(noFB = "No Feedback", FB = "Feedback")) +
  theme_classic() +
  labs(x = "Condition", y = "Median(error) with 95% bootstrap CI")

# Define the 20 degree signed fb_offset bins for plotting purposes
fb_data <- train %>%
  filter(condition == "FB")
offset_bin_breaks <- seq(-180, 180, by = 20)
offset_bin_labels <- paste(head(offset_bin_breaks, -1), tail(offset_bin_breaks, -1), sep = "-")
offset_bins <- cut(
  fb_data$fb_offset, breaks = offset_bin_breaks,
  include.lowest = TRUE, labels = offset_bin_labels
)

# Compute the median error per fb_offset bin
offset_median_boot_by_bin <- fb_data %>%
  mutate(offset_bin = offset_bins) %>%
  group_by(offset_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error vs. fb_offset
plot_D <- ggplot(offset_median_boot_by_bin, aes(x = offset_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Visual feedback offset", y = "Median(error) with 95% bootstrap CI")

plot_C
plot_D

# Does error's median differ between noFB and FB conditions?
# Controlled for subjects
condition_median_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  median(samp$error[samp$condition == "FB"]) - median(samp$error[samp$condition == "noFB"])
}, R = R_boot)
condition_median_diff_ci <- boot.ci(condition_median_diff_boot, type = "perc")$percent[4:5]

# Does median error differ between mirrored positive/negative offset bins on average?
# Controlled for subjects
n_offset_bins <- length(offset_bin_labels)
offset_data <- fb_data %>% mutate(offset_bin = offset_bins)
offset_mirror_pos_bins <- offset_bin_labels[(n_offset_bins / 2 + 1):n_offset_bins]
offset_mirror_neg_bins <- rev(offset_bin_labels[1:(n_offset_bins / 2)])
offset_mirror_median_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ offset_data %>% filter(subj == .x))
  mean(map2_dbl(offset_mirror_pos_bins, offset_mirror_neg_bins, ~ {
    median(samp$error[samp$offset_bin == .x]) - median(samp$error[samp$offset_bin == .y])
  }))
}, R = R_boot)
offset_mirror_median_diff_ci <- boot.ci(offset_mirror_median_diff_boot, type = "perc")$percent[4:5]
```

- Median error was higher in trials where visual feedback was provided (bootstrapped 95% CI of difference between two conditions = [`r round(condition_median_diff_ci[1], 2)`, `r round(condition_median_diff_ci[2], 2)`]$^\circ$), consistent with varying reliability of the visual feedback (@fig-error-by-condition-offset-1). The above deviation from the forced fusion model based on a normative Bayesian observer has been shown before where the observers have a tendency to overweight signals from a sensory modality (vision) which can provide better information than their own proprioceptive sense [@Noppeney_2021].
- Median error is low for reliable visual feedback (low offsets), increases rapidly for positive offsets till around 60$^\circ$ and decreases thereafter (@fig-error-by-condition-offset-2). On the other hand, error increases gradually for negative offsets, plateaus around 60$^\circ$, then increases again (@fig-error-by-condition-offset-2). Thus, participants' responses may be affected by the direction of the feedback offset (mirrored positive vs. negative bins, bootstrapped 95% CI of difference = [`r round(offset_mirror_median_diff_ci[1], 2)`, `r round(offset_mirror_median_diff_ci[2], 2)`]$^\circ$) along with it's reliability. The extent of integration between proprioception and vision depends on the size of the conflict between the information from both sources [@Noppeney_2021].

```{r}
#| label: fig-error-variance
#| fig-cap: "**SD of error across target heading bins, condition, and visual feedback offset magnitude**"
#| fig-subcap: true
#| layout-ncol: 3
#| code-summary: ""
#| code-fold: true
#| fig-width: 4
#| fig-height: 5

# Does the variance of error grow across target bins?
# Controlling for individual subjects
error_sd_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error's SD vs. target
plot_E <- ggplot(error_sd_boot_by_bin, aes(x = target_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "SD(error) with 95% bootstrap CI")

# Does error's SD differ between noFB and FB conditions?
# Controlled for subjects
condition_sd_boot <- train %>%
  group_by(condition) %>%
  group_modify(~ {
    group_data <- .x
    group_subjs <- unique(group_data$subj)
    b <- boot(group_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ group_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error's SD vs. condition
plot_F <- ggplot(condition_sd_boot, aes(x = condition, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(labels = c(noFB = "No Feedback", FB = "Feedback")) +
  theme_classic() +
  labs(x = "Condition", y = "SD(error) with 95% bootstrap CI")

# Does error's SD grow with fb_offset?
# Controlled for subjects
offset_sd_boot_by_bin <- fb_data %>%
  mutate(offset_bin = offset_bins) %>%
  group_by(offset_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error's SD vs. fb_offset
plot_G <- ggplot(offset_sd_boot_by_bin, aes(x = offset_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Visual feedback offset", y = "SD(error) with 95% bootstrap CI")

plot_E
plot_F
plot_G

# Does error's SD differ between noFB and FB conditions? (magnitude of the difference)
# Controlled for subjects
condition_sd_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  sd(samp$error[samp$condition == "FB"]) - sd(samp$error[samp$condition == "noFB"])
}, R = R_boot)
condition_sd_diff_ci <- boot.ci(condition_sd_diff_boot, type = "perc")$percent[4:5]

# Does error's SD differ between mirrored positive/negative offset bins on average?
# Controlled for subjects
offset_mirror_sd_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ offset_data %>% filter(subj == .x))
  mean(map2_dbl(offset_mirror_pos_bins, offset_mirror_neg_bins, ~ {
    sd(samp$error[samp$offset_bin == .x]) - sd(samp$error[samp$offset_bin == .y])
  }))
}, R = R_boot)
offset_mirror_sd_diff_ci <- boot.ci(offset_mirror_sd_diff_boot, type = "perc")$percent[4:5]

# Does |error| (1/accuracy) change with viewAmount (attention paid to the feedback cue)?
# FB trials only; controlled for subjects
accuracy_view_amount_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ fb_data %>% filter(subj == .x))
  coef(rq(abs(error) ~ viewAmount, tau = 0.5, data = samp))["viewAmount"]
}, R = R_boot)
accuracy_view_amount_slope_ci <- boot.ci(accuracy_view_amount_slope_boot, type = "perc")$percent[4:5]
```

- Standard deviation (SD) of error maybe a measure of uncertainity about the information. As @fig-error-variance-1 shows, SD of error grows with task difficulty, but it rises in two phases separated by a plateau in the range of 120$^\circ$ to 240$^\circ$.
- The amount of uncertainity was higher in trials where visual feedback was provided (bootstrapped 95% CI of difference = [`r round(condition_sd_diff_ci[1], 2)`, `r round(condition_sd_diff_ci[2], 2)`]$^\circ$) (@fig-error-variance-2).
- The amount of uncertainity rises with unreliability of the visual feedback but plateaus around 60$^\circ$ for both positive and negative offsets (@fig-error-variance-3). The uncertainity might be tracking the reliability of the visual feedback reinforcing the impact of conflict size on integration of visual and proprioceptive information. The uncertainity is higher for negative feedback offsets as compared to the corresponding positive offsets (mirrored positive vs. negative bins, bootstrapped 95% CI of difference = [`r round(offset_mirror_sd_diff_ci[1], 2)`, `r round(offset_mirror_sd_diff_ci[2], 2)`]$^\circ$).

```{r}
#| label: fig-error-by-trial-duration
#| fig-cap: "**Median and SD of error across trial duration deciles**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Define the trial_duration decile bins for plotting purposes
duration_bin_breaks <- quantile(train$trial_duration, probs = seq(0, 1, by = 0.1))
# Label bins in seconds for readability; computation stays in msec
duration_bin_labels <- paste(head(round(duration_bin_breaks / 1000, 1), -1), tail(round(duration_bin_breaks / 1000, 1), -1), sep = "-")
duration_bins <- cut(
  train$trial_duration, breaks = duration_bin_breaks,
  include.lowest = TRUE, labels = duration_bin_labels
)

# Compute the median of error per trial_duration bin
plot_error_by_duration <- train %>%
  mutate(duration_bin = duration_bins) %>%
  group_by(duration_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  }) %>%
    # Build the plot
    ggplot(aes(x = duration_bin, y = median)) +
    geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "trial duration (sec)", y = "Median(error) with 95% bootstrap CI")

# Compute the SD of error per trial_duration bin
plot_error_sd_by_duration <- train %>%
  mutate(duration_bin = duration_bins) %>%
  group_by(duration_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  }) %>%
    # Build the plot
    ggplot(aes(x = duration_bin, y = sd)) +
    geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "trial duration (sec)", y = "SD(error) with 95% bootstrap CI")

plot_error_by_duration
plot_error_sd_by_duration

# Does error's median grow with trial_duration?
# Controlled for subjects
duration_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(error ~ trial_duration, tau = 0.5, data = samp))["trial_duration"]
}, R = R_boot)
duration_slope_ci <- boot.ci(duration_slope_boot, type = "perc")$percent[4:5]
```

- Median error does not depend on trial duration (bootstrapped 95% CI for median regression slope [`r format(round(duration_slope_ci[1], 4), scientific = FALSE)`, `r format(round(duration_slope_ci[2], 4), scientific = FALSE)`]$^\circ$/msec) (@fig-error-by-trial-duration-1), but the uncertainity grows with trial duration (@fig-error-by-trial-duration-2).

```{r}
#| label: fig-error-by-fb-time
#| fig-cap: "**Median and SD of error across different times (deciles) the feedback was displayed**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Define the fb_time decile bins for plotting purposes, FB trials only
fb_time_bin_breaks <- quantile(fb_data$fb_time, probs = seq(0, 1, by = 0.1))
# Label bins in seconds for readability; computation stays in msec
fb_time_bin_labels <- paste(head(round(fb_time_bin_breaks / 1000, 1), -1), tail(round(fb_time_bin_breaks / 1000, 1), -1), sep = "-")
fb_time_bins <- cut(
  fb_data$fb_time, breaks = fb_time_bin_breaks,
  include.lowest = TRUE, labels = fb_time_bin_labels
)

# Compute the median of error per fb_time bin
plot_error_by_fb_time <- fb_data %>%
  mutate(fb_time_bin = fb_time_bins) %>%
  group_by(fb_time_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  }) %>%
    # Build the plot
    ggplot(aes(x = fb_time_bin, y = median)) +
    geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "feedback display time (sec)", y = "Median(error) with 95% bootstrap CI")

# Compute the SD of error per fb_time bin
plot_error_sd_by_fb_time <- fb_data %>%
  mutate(fb_time_bin = fb_time_bins) %>%
  group_by(fb_time_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  }) %>%
    # Build the plot
    ggplot(aes(x = fb_time_bin, y = sd)) +
    geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "feedback display time (sec)", y = "SD(error) with 95% bootstrap CI")

plot_error_by_fb_time
plot_error_sd_by_fb_time

# Does error's median grow with fb_time?
fb_time_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ fb_data %>% filter(subj == .x))
  coef(rq(error ~ fb_time, tau = 0.5, data = samp))["fb_time"]
}, R = R_boot)
fb_time_slope_ci <- boot.ci(fb_time_slope_boot, type = "perc")$percent[4:5]
```

- Similarly, median error does not depend on when the feedback was displayed (bootstrapped 95% CI for median regression slope [`r format(round(fb_time_slope_ci[1], 4), scientific = FALSE)`, `r format(round(fb_time_slope_ci[2], 4), scientific = FALSE)`]$^\circ$/msec) (@fig-error-by-fb-time-1), but the uncertainity is less when the feedback is displayed earlier rather than later (@fig-error-by-fb-time-2).

From the above characteristics of the participants' responses, it is clear that the magnitude of error depends on both the proprioceptive and visual information. The final perceptual estimate is computed by averaging the individual estimates weighted by their reliabilities [@Noppeney_2021], but this may or may not happen in a normative manner depending on the size of the conflict between the two information sources. The uncertainity depends on task difficulty (`target`), trial duration, presence or absence of visual feedback, reliability of the visual feedback (`|fb_offset|`), direction of the offset, and the time when the feedback was displayed.  

Accuracy (1/`|error|`) improves as attention increases (`viewAmount` decreases) (bootstrapped 95% CI for the median regression slope [`r round(accuracy_view_amount_slope_ci[1], 3)`, `r round(accuracy_view_amount_slope_ci[2], 3)`]). The accuracy of the best model will be validated against this behavioral characteritic.  

### Subjective Measure (make it more descriptive)

```{r}
#| label: fig-conf-by-target
#| fig-cap: "**Median and SD of subjective confidence across target heading bins**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Compute the median of conf per target bins
conf_median_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$conf)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for conf vs. target
plot_H <- ggplot(conf_median_boot_by_bin, aes(x = target_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "Median(conf) with 95% bootstrap CI")

# Does subjective confidence (conf) grow with target (task difficulty)?
# Controlled for subjects
conf_target_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(conf ~ target, tau = 0.5, data = samp))["target"]
}, R = R_boot)
conf_target_slope_ci <- boot.ci(conf_target_slope_boot, type = "perc")$percent[4:5]

# Does conf's SD also grow with target?
# Controlling for individual subjects
conf_sd_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$conf)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for conf's SD vs. target
plot_I <- ggplot(conf_sd_boot_by_bin, aes(x = target_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "SD(conf) with 95% bootstrap CI")

plot_H
plot_I

# Does conf track |error| ie. 1/accuracy?
# Controlled for subjects
conf_error_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(conf ~ abs(error), tau = 0.5, data = samp))["abs(error)"]
}, R = R_boot)
conf_error_slope_ci <- boot.ci(conf_error_slope_boot, type = "perc")$percent[4:5]
```

- Subjective confidence reduces with task difficulty (bootstrapped 95% CI for the median regression slope [`r round(conf_target_slope_ci[1], 3)`, `r round(conf_target_slope_ci[2], 3)`]) similar to error which is an objective measure of performance (@fig-conf-by-target-1).
- But SD of this subjective measure does not grow with task difficulty (@fig-conf-by-target-2).
- Confidence does not track performance accuracy (1/`|error|`) (bootstrapped 95% CI for the median regression slope [`r round(conf_error_slope_ci[1], 3)`, `r round(conf_error_slope_ci[2], 3)`]).

Thus, participants track their performance based on the task's difficulty and not on how well they actually did. The winning model's internal uncertainity measure will be validated against these behavioral characteristics.  

## Models (descriptive title later)

```{r}
#| label: error-median-mean-diff
#| code-summary: ""
#| code-fold: true
#| message: false

# Is error's median different from it's mean, controlling for individual subjects?
median_mean_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  median(samp$error) - mean(samp$error)
}, R = R_boot)
median_mean_diff_ci <- boot.ci(median_mean_diff_boot, type = "perc")$percent[4:5]
```

Main goal was to create a generalizable linear model which can track it's own uncertainity, offering an alternative to the nonlinear path integration and cue combination models defined in the source paper [@Harootonian_2022]. GAMLSS [@R.A.Rigby_2005] was chosen since the scale ($\sigma$) and shape ($\nu$) can be modelled against task variables. This was necessary here to capture how uncertainity scales with task difficulty, presence or absence of feedback, reliability of the feedback and other time-related variables. The skew-normal (`SN2`) distribution family is used, since error's median is less than it's mean even across subjects (bootstrapped 95% CI for median(error) - mean(error) [`r round(median_mean_diff_ci[1], 3)`, `r round(median_mean_diff_ci[2], 3)`]$^\circ$). Each model's predictors were tuned based on 5-fold cross validation across the training set containing data from `r length(unique(train$subj))` participants.

### Unisensory Model

$$
\begin{aligned}
\text{error} &\sim SN2(\mu, \sigma, \nu) \\
\mu &= \beta_0 + b_{subj} \\
\sigma &= \gamma_0 + \gamma_1 \; \text{target} + b_{subj} \\
\nu &= \delta_0 + \delta_1 \; \text{target} + \delta_2 \; \text{trial\_duration} + b_{subj}
\end{aligned}
$$

```{r}
#| label: fig-model-unisensory
#| fig-cap: "**Unisensory model: Predicted SD of error against target (line: median trial duration, shaded band: 10th-90th percentile trial duration), and predictor collinearity (adjusted GVIF)**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: Fit unisensory model
#| code-fold: true
#| message: false
#| fig-width: 5
#| fig-height: 6

# Define the number of cycles to run for modelling and non-verbose output
gamlss_control <- gamlss.control(n.cyc = 300, trace = FALSE)

# Define the model
# Internal representation of the rotation
unisensory_formula <- error ~ 1 + re(random = ~1|subj, level = 0) # subj as a random intercept
# Skew-normal distribution for error
unisensory_family <- SN2()

# Winning formulas from cross-validated comparison (cv-unisensory.rds)
# SD ie. noise: target only
unisensory_sigma_formula <- ~ target + re(random = ~1|subj, level = 0)
# Skewness: target + trial_duration
unisensory_nu_formula <- ~ target + trial_duration + re(random = ~1|subj, level = 0)

# Fit the model
unisensory <- gamlss(
  formula = unisensory_formula,
  sigma.formula = unisensory_sigma_formula,
  nu.formula = unisensory_nu_formula,
  family = unisensory_family,
  data = train,
  control = gamlss_control
)

# Tidy labels for the collinearity predictors
unisensory_term_labels <- c(target = "Target Heading", trial_duration = "Trial Duration", subj = "Participant")

# Check collinearity between the winning predictors, controlling for subj
unisensory_vif <- vif(lm(error ~ target + trial_duration + subj, data = train))
# Keep only the adjusted GVIF column as a table grob
unisensory_vif_table <- unisensory_vif[, "GVIF^(1/(2*Df))", drop = FALSE] %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  mutate(term = unisensory_term_labels[term]) %>%
  rename(Term = term, `Adjusted GVIF` = `GVIF^(1/(2*Df))`) %>%
  mutate(`Adjusted GVIF` = round(`Adjusted GVIF`, 2)) %>%
  tableGrob(rows = NULL, theme = ttheme_default(base_size = 16))

# Predicted SD of error across target, at a fixed trial_duration
predict_unisensory_sd <- function(trial_duration_value) {
  newdata <- tibble(target = seq(0, 360, length.out = 200),
                     trial_duration = trial_duration_value,
                     subj = factor("population"))
  pred_sigma <- predict(unisensory, what = "sigma", newdata = newdata, type = "response", data = train)
  pred_nu <- predict(unisensory, what = "nu", newdata = newdata, type = "response", data = train)
  # True SD of the fitted SN2 error distribution, from the family's own variance function
  sqrt(unisensory_family$variance(mu = 0, sigma = pred_sigma, nu = pred_nu))
}

# Predicted SD at the 10th/50th/90th percentile trial_duration, since nu depends on it too
unisensory_pred_by_target <- tibble(
  target = seq(0, 360, length.out = 200),
  lo = predict_unisensory_sd(quantile(train$trial_duration, 0.1)),
  median = predict_unisensory_sd(quantile(train$trial_duration, 0.5)),
  hi = predict_unisensory_sd(quantile(train$trial_duration, 0.9))
)

# Plot predicted SD vs. target, median line with a ribbon spanning the 10th-90th percentile trial_duration
unisensory_plot_sigma_target <- unisensory_pred_by_target %>%
  ggplot(aes(x = target, y = median)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.2) +
  geom_line(colour = "steelblue4", linewidth = 1) +
  theme_classic() +
  labs(x = "Target Heading", y = "Predicted SD of error")

# KS test of residuals against the theoretical normal distribution
unisensory_ks <- ks.test(resid(unisensory), "pnorm", mean(resid(unisensory)), sd(resid(unisensory)))

unisensory_plot_sigma_target
grid.arrange(unisensory_vif_table)
```

This model assumes that all trials were performed using only the proprioceptive information perceived at the end of encoding period and during the retrieval period. Visual feedback has no bearing on the participant's responses. The uncertainity of the predicted value increases with task difficulty (@fig-model-unisensory-1), consistent with the behavioral relationship between error and target. But the residuals do not align with a normal distribution (Kolmogorov-Smirnov test D = `r round(unisensory_ks$statistic, 3)`, p `r ifelse(unisensory_ks$p.value < 0.001, "< 0.001", paste("=", round(unisensory_ks$p.value, 3)))`). Will just the presence of visual feedback improve this?

### Naive Multisensory Model

$$
\begin{aligned}
\text{error} &\sim SN2(\mu, \sigma, \nu) \\
\mu &= \beta_0 + \beta_1 \; \text{condition} + b_{subj} \\
\sigma &= \gamma_0 + \gamma_1 \; \text{target} + \gamma_2 \; \text{trial\_duration} + \gamma_3 \; \text{condition} \\
&\quad + \gamma_4 \; (\text{target} \cdot \text{condition}) + \gamma_5 \; (\text{trial\_duration} \cdot \text{condition}) + b_{subj} \\
\nu &= \delta_0 + \delta_1 \; \text{target} + \delta_2 \; \text{trial\_duration} + \delta_3 \; \text{condition} + b_{subj}
\end{aligned}
$$

```{r}
#| label: fig-model-naive-multisensory
#| fig-cap: "**Naive multisensory model: Predicted SD of error against target by condition (line: median trial duration, shaded band: 10th-90th percentile trial duration), and predictor collinearity (adjusted GVIF)**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: Fit naive multisensory model
#| code-fold: true
#| message: false
#| fig-width: 5
#| fig-height: 6

# Define the model
# Winning formulas from cross-validated comparison (cv-naive-multisensory.rds)
# Location: shifts by presence of visual feedback
naive_multisensory_formula <- error ~ condition + re(random = ~1|subj, level = 0)
# SD ie. noise: (target + trial_duration) * condition
naive_multisensory_sigma_formula <- ~ (target + trial_duration) * condition + re(random = ~1|subj, level = 0)
# Skewness: target + trial_duration + condition
naive_multisensory_nu_formula <- ~ target + trial_duration + condition + re(random = ~1|subj, level = 0)
# Skew-normal distribution for error
naive_multisensory_family <- SN2()

# Fit the model
naive_multisensory <- gamlss(
  formula = naive_multisensory_formula,
  sigma.formula = naive_multisensory_sigma_formula,
  nu.formula = naive_multisensory_nu_formula,
  family = naive_multisensory_family,
  data = train,
  control = gamlss_control
)

# Tidy labels for the collinearity predictors
naive_multisensory_term_labels <- c(target = "Target Heading", trial_duration = "Trial Duration",
                                     condition = "Condition", subj = "Participant")

# Check collinearity between the winning predictors and their interaction with condition, controlling for subj
naive_multisensory_vif <- vif(lm(error ~ (target + trial_duration) * condition + subj, data = train), type = "predictor")
# Keep only the adjusted GVIF column as a table grob
naive_multisensory_vif_table <- naive_multisensory_vif[, "GVIF^(1/(2*Df))", drop = FALSE] %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  mutate(term = naive_multisensory_term_labels[term]) %>%
  rename(Term = term, `Adjusted GVIF` = `GVIF^(1/(2*Df))`) %>%
  mutate(`Adjusted GVIF` = round(`Adjusted GVIF`, 2)) %>%
  tableGrob(rows = NULL, theme = ttheme_default(base_size = 16))

# Predicted SD of error across target, at a fixed trial_duration and condition
predict_naive_multisensory_sd <- function(trial_duration_value, condition_value) {
  newdata <- tibble(target = seq(0, 360, length.out = 200),
                     trial_duration = trial_duration_value,
                     condition = factor(condition_value, levels = levels(train$condition)),
                     subj = factor("population"))
  pred_sigma <- predict(naive_multisensory, what = "sigma", newdata = newdata, type = "response", data = train)
  pred_nu <- predict(naive_multisensory, what = "nu", newdata = newdata, type = "response", data = train)
  # True SD of the fitted SN2 error distribution, from the family's own variance function
  sqrt(naive_multisensory_family$variance(mu = 0, sigma = pred_sigma, nu = pred_nu))
}

# Predicted SD at the 10th/50th/90th percentile trial_duration, since nu depends on it too, per condition
naive_multisensory_pred_by_target <- map_dfr(levels(train$condition), function(cond) {
  tibble(
    target = seq(0, 360, length.out = 200),
    condition = cond,
    lo = predict_naive_multisensory_sd(quantile(train$trial_duration, 0.1), cond),
    median = predict_naive_multisensory_sd(quantile(train$trial_duration, 0.5), cond),
    hi = predict_naive_multisensory_sd(quantile(train$trial_duration, 0.9), cond)
  )
})

# Plot predicted SD vs. target, median line with a ribbon spanning the 10th-90th percentile trial_duration, by condition
naive_multisensory_plot_sigma_target <- naive_multisensory_pred_by_target %>%
  ggplot(aes(x = target, y = median, colour = condition, fill = condition)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.2, colour = NA) +
  geom_line(linewidth = 1) +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  labs(x = "Target Heading", y = "Predicted SD of error", colour = "Condition", fill = "Condition")

# KS test of residuals against the theoretical normal distribution
naive_multisensory_ks <- ks.test(resid(naive_multisensory), "pnorm", mean(resid(naive_multisensory)), sd(resid(naive_multisensory)))

naive_multisensory_plot_sigma_target
grid.arrange(naive_multisensory_vif_table)
```

This model assumes that all trials were performed using proprioceptive information without discounting the presence of visual feedback. Visual feedback's reliability has no bearing on the participant's responses. The uncertainity of the predicted value increases with task difficulty and with addition of feedback (@fig-model-naive-multisensory-1), consistent with the behavioral relationship between error and condition. The residuals almost align with a normal distribution (Kolmogorov-Smirnov test D = `r round(naive_multisensory_ks$statistic, 3)`, p `r ifelse(naive_multisensory_ks$p.value < 0.001, "< 0.001", paste("=", round(naive_multisensory_ks$p.value, 3)))`). How does adding information about reliability of the visual feedback change this model?

### Multisensory Model

$$
\begin{aligned}
\text{error} &\sim SN2(\mu, \sigma, \nu) \\
\mu &= \beta_0 + \beta_1 \; \text{condition} + b_{subj} \\
\sigma &= \gamma_0 + \gamma_1 \; \text{target} + \gamma_2 \; \text{trial\_duration} + \gamma_3 \; \text{fb\_offset} \\
&\quad + \gamma_4 \; (\text{trial\_duration} \cdot \text{fb\_offset}) + b_{subj} \\
\nu &= \delta_0 + \delta_1 \; \text{target} + \delta_2 \; \text{trial\_duration} + \delta_3 \; \text{fb\_offset} + \delta_4 \; \text{fb\_time} \\
&\quad + \delta_5 \; (\text{trial\_duration} \cdot \text{fb\_offset}) + b_{subj}
\end{aligned}
$$

```{r}
#| label: fig-model-multisensory
#| fig-cap: "**Multisensory model: Predicted SD of error against target heading by feedback offset level, and against feedback offset by target heading, both faceted by trial duration level**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: Fit multisensory model
#| code-fold: true
#| message: false
#| fig-width: 5
#| fig-height: 6

# Define the model
# Winning formulas from cross-validated comparison (cv-multisensory.rds, cv-multisensory-interactions.rds, cv-multisensory-condition.rds)
# Location: shifts by condition, not by signed feedback offset
multisensory_formula <- error ~ condition + re(random = ~1|subj, level = 0)
# SD ie. noise: target + trial_duration + fb_offset, with a trial_duration:fb_offset interaction
multisensory_sigma_formula <- ~ target + trial_duration + fb_offset + trial_duration:fb_offset + re(random = ~1|subj, level = 0)
# Skewness: target + trial_duration + fb_offset + trial_duration:fb_offset + fb_time, dropping target:fb_offset
multisensory_nu_formula <- ~ target + trial_duration + fb_offset + trial_duration:fb_offset + fb_time + re(random = ~1|subj, level = 0)
# Skew-normal distribution for error
multisensory_family <- SN2()

# Fit the model
multisensory <- gamlss(
  formula = multisensory_formula,
  sigma.formula = multisensory_sigma_formula,
  nu.formula = multisensory_nu_formula,
  family = multisensory_family,
  data = train,
  control = gamlss_control
)

# NLL to compare against the CV-winning formula that included target:fb_offset in nu
multisensory_nll <- -sum(dSN2(train$error,
                               mu = fitted(multisensory, what = "mu"),
                               sigma = fitted(multisensory, what = "sigma"),
                               nu = fitted(multisensory, what = "nu"),
                               log = TRUE))

# Tidy labels for the collinearity predictors
multisensory_term_labels <- c(target = "Target Heading", trial_duration = "Trial Duration",
                               fb_offset = "Feedback Offset", fb_time = "Feedback Time", subj = "Participant")

# Check collinearity between the winning predictors and their interactions with fb_offset, controlling for subj
multisensory_vif <- vif(lm(error ~ target * fb_offset + trial_duration * fb_offset + fb_time + subj, data = train), type = "predictor")
# Keep only the adjusted GVIF column as a table grob
multisensory_vif_table <- multisensory_vif[, "GVIF^(1/(2*Df))", drop = FALSE] %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  mutate(term = multisensory_term_labels[term]) %>%
  rename(Term = term, `Adjusted GVIF` = `GVIF^(1/(2*Df))`) %>%
  mutate(`Adjusted GVIF` = round(`Adjusted GVIF`, 2)) %>%
  tableGrob(rows = NULL, theme = ttheme_default(base_size = 16))

multisensory_target_values <- c(0, 90, 180, 270)
multisensory_duration_levels <- round(quantile(train$trial_duration, c(0.1, 0.5, 0.9)))
multisensory_offset_levels <- seq(-180, 180, by = 60)

# Grid with target, trial_duration and fb_offset all varying, fb_time fixed at its median
multisensory_pred_by_target <- expand_grid(target = multisensory_target_values,
                                            trial_duration = multisensory_duration_levels,
                                            fb_offset = multisensory_offset_levels,
                                            fb_time = median(train$fb_time),
                                            subj = factor("population")) %>%
  mutate(pred_sigma = suppressWarnings(predict(multisensory, what = "sigma", newdata = ., type = "response", data = train)),
         pred_nu = suppressWarnings(predict(multisensory, what = "nu", newdata = ., type = "response", data = train)),
         pred_sd = sqrt(multisensory_family$variance(mu = 0, sigma = pred_sigma, nu = pred_nu)),
         duration_label = factor(trial_duration, levels = multisensory_duration_levels,
                                  labels = paste0("Trial Duration = ", round(multisensory_duration_levels / 1000, 1), " s")),
         offset_label = factor(fb_offset))

# Grid with target, trial_duration and fb_offset all varying, fb_time fixed at its median
multisensory_offset_seq <- seq(-180, 180, length.out = 200)
multisensory_pred_by_offset <- expand_grid(target = multisensory_target_values,
                                            trial_duration = multisensory_duration_levels,
                                            fb_offset = multisensory_offset_seq,
                                            fb_time = median(train$fb_time),
                                            subj = factor("population")) %>%
  mutate(pred_sigma = suppressWarnings(predict(multisensory, what = "sigma", newdata = ., type = "response", data = train)),
         pred_nu = suppressWarnings(predict(multisensory, what = "nu", newdata = ., type = "response", data = train)),
         pred_sd = sqrt(multisensory_family$variance(mu = 0, sigma = pred_sigma, nu = pred_nu)),
         target = factor(target),
         duration_label = factor(trial_duration, levels = multisensory_duration_levels,
                                  labels = paste0("Trial Duration = ", round(multisensory_duration_levels / 1000, 1), " s")))

# Plot predicted SD vs. target by fb_offset level, faceted by trial_duration level
multisensory_plot_sigma_target <- multisensory_pred_by_target %>%
  ggplot(aes(x = target, y = pred_sd, colour = offset_label)) +
  geom_line(linewidth = 1) +
  facet_wrap(~ duration_label, ncol = 3) +
  scale_colour_brewer(palette = "RdBu") +
  theme_classic() +
  theme(legend.position = "inside", legend.position.inside = c(1, 0), legend.justification = c(1, 0)) +
  labs(x = "Target Heading", y = "Predicted SD of error", colour = "Feedback Offset")

# Plot predicted SD vs. fb_offset by target, faceted by trial_duration level
multisensory_plot_sigma_offset <- multisensory_pred_by_offset %>%
  ggplot(aes(x = fb_offset, y = pred_sd, colour = target)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = c(-60, 60), linetype = "dashed") +
  facet_wrap(~ duration_label, ncol = 3) +
  scale_colour_brewer(palette = "Blues") +
  theme_classic() +
  theme(legend.position = "inside", legend.position.inside = c(1, 0), legend.justification = c(1, 0)) +
  labs(x = "Feedback Offset", y = "Predicted SD of error", colour = "Target Heading")

# KS test of residuals against the theoretical normal distribution
multisensory_ks <- ks.test(resid(multisensory), "pnorm", mean(resid(multisensory)), sd(resid(multisensory)))

multisensory_plot_sigma_target
multisensory_plot_sigma_offset
```

```{r}
#| label: fig-model-multisensory-vif
#| fig-cap: "**Predictor collinearity**"
#| code-summary: ""
#| code-fold: true
#| message: false
#| fig-width: 5
#| fig-height: 2

grid.arrange(multisensory_vif_table)
```

This model assumes that all trials were performed using proprioceptive information without discounting the reliability of the visual feedback. The uncertainity increases with task difficulty and the effect of reliability depends on the time taken to respond and offset's direction (@fig-model-multisensory-1). For lower trial durations, negative offsets show higher uncertainity (@fig-model-multisensory-2), consistent with the behavioral relationship between error and feedback offset. As trial duration increases, the multisensory model shows similar uncertainity for negative and positive offsets. The residuals are even closer to a normal distribution (Kolmogorov-Smirnov test D = `r round(multisensory_ks$statistic, 3)`, p `r ifelse(multisensory_ks$p.value < 0.001, "< 0.001", paste("=", round(multisensory_ks$p.value, 3)))`). The plateau in uncertainity at 60$^\circ$ of feedback offset is not seen in this. Could the brain be switching between segregation and integration depending on the conflict size of information received from properioception and vision?

### Hybrid Model

```{r}
#| label: fig-model-hybrid
#| fig-cap: "**Hybrid model: Precision-weighted predicted SD of error against target heading by feedback offset level, and against feedback offset by target heading, both faceted by trial duration level**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: Combine unisensory and multisensory model predictions
#| code-fold: true
#| message: false
#| fig-width: 5
#| fig-height: 6

# Same grid as the multisensory plots: target, trial_duration and fb_offset all varying, fb_time at its median
hybrid_pred_by_target <- expand_grid(target = multisensory_target_values,
                                      trial_duration = multisensory_duration_levels,
                                      fb_offset = multisensory_offset_levels,
                                      fb_time = median(train$fb_time),
                                      condition = factor("FB", levels = levels(train$condition)),
                                      subj = factor("population")) %>%
  mutate(uni_sigma = predict(unisensory, what = "sigma", newdata = ., type = "response", data = train),
         uni_nu = predict(unisensory, what = "nu", newdata = ., type = "response", data = train),
         uni_sd = sqrt(unisensory_family$variance(mu = 0, sigma = uni_sigma, nu = uni_nu)),
         multi_sigma = suppressWarnings(predict(multisensory, what = "sigma", newdata = ., type = "response", data = train)),
         multi_nu = suppressWarnings(predict(multisensory, what = "nu", newdata = ., type = "response", data = train)),
         multi_sd = sqrt(multisensory_family$variance(mu = 0, sigma = multi_sigma, nu = multi_nu)),
         # Precision-weighted combination of each model's predicted SD
         pred_sd = sqrt(1 / (1 / uni_sd^2 + 1 / multi_sd^2)),
         duration_label = factor(trial_duration, levels = multisensory_duration_levels,
                                  labels = paste0("Trial Duration = ", round(multisensory_duration_levels / 1000, 1), " s")),
         offset_label = factor(fb_offset))

# Define the plot for predicted SD vs. target by fb_offset level, faceted by trial_duration level
hybrid_plot_sigma_target <- hybrid_pred_by_target %>%
  ggplot(aes(x = target, y = pred_sd, colour = offset_label)) +
  geom_line(linewidth = 1) +
  facet_wrap(~ duration_label, ncol = 3) +
  scale_colour_brewer(palette = "RdBu") +
  theme_classic() +
  theme(legend.position = "inside", legend.position.inside = c(1, 0), legend.justification = c(1, 0)) +
  labs(x = "Target Heading", y = "Predicted SD of error", colour = "Feedback Offset")

# Same grid as the multisensory plots: target, trial_duration and fb_offset all varying, fb_time at its median
hybrid_pred_by_offset <- expand_grid(target = multisensory_target_values,
                                      trial_duration = multisensory_duration_levels,
                                      fb_offset = multisensory_offset_seq,
                                      fb_time = median(train$fb_time),
                                      condition = factor("FB", levels = levels(train$condition)),
                                      subj = factor("population")) %>%
  mutate(uni_sigma = predict(unisensory, what = "sigma", newdata = ., type = "response", data = train),
         uni_nu = predict(unisensory, what = "nu", newdata = ., type = "response", data = train),
         uni_sd = sqrt(unisensory_family$variance(mu = 0, sigma = uni_sigma, nu = uni_nu)),
         multi_sigma = suppressWarnings(predict(multisensory, what = "sigma", newdata = ., type = "response", data = train)),
         multi_nu = suppressWarnings(predict(multisensory, what = "nu", newdata = ., type = "response", data = train)),
         multi_sd = sqrt(multisensory_family$variance(mu = 0, sigma = multi_sigma, nu = multi_nu)),
         # Precision-weighted combination of each model's predicted SD
         pred_sd = sqrt(1 / (1 / uni_sd^2 + 1 / multi_sd^2)),
         target = factor(target),
         duration_label = factor(trial_duration, levels = multisensory_duration_levels,
                                  labels = paste0("Trial Duration = ", round(multisensory_duration_levels / 1000, 1), " s")))

# Define the plot for predicted SD vs. fb_offset by target, faceted by trial_duration level
hybrid_plot_sigma_offset <- hybrid_pred_by_offset %>%
  ggplot(aes(x = fb_offset, y = pred_sd, colour = target)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = c(-60, 60), linetype = "dashed") +
  facet_wrap(~ duration_label, ncol = 3) +
  scale_colour_brewer(palette = "Blues") +
  theme_classic() +
  theme(legend.position = "inside", legend.position.inside = c(1, 0), legend.justification = c(1, 0)) +
  labs(x = "Feedback Offset", y = "Predicted SD of error", colour = "Target Heading")

hybrid_plot_sigma_target
hybrid_plot_sigma_offset

# Per-trial predicted SD beyond the -60 to 60 feedback offset band, where uncertainity behaviorally plateaus
hybrid_offset_diff_data <- train %>%
  filter(fb_offset < -60 | fb_offset > 60) %>%
  mutate(multi_sigma = suppressWarnings(predict(multisensory, what = "sigma", newdata = ., type = "response", data = train)),
         multi_nu = suppressWarnings(predict(multisensory, what = "nu", newdata = ., type = "response", data = train)),
         multisensory_sd = sqrt(multisensory_family$variance(mu = 0, sigma = multi_sigma, nu = multi_nu)),
         uni_sigma = predict(unisensory, what = "sigma", newdata = ., type = "response", data = train),
         uni_nu = predict(unisensory, what = "nu", newdata = ., type = "response", data = train),
         uni_sd = sqrt(unisensory_family$variance(mu = 0, sigma = uni_sigma, nu = uni_nu)),
         hybrid_sd = sqrt(1 / (1 / uni_sd^2 + 1 / multisensory_sd^2)),
         diff_sd = hybrid_sd - multisensory_sd)

# Paired mean difference (hybrid - multisensory) within the band, as mean +/- 2 SE
hybrid_offset_diff_mean <- mean(hybrid_offset_diff_data$diff_sd)
hybrid_offset_diff_se <- sd(hybrid_offset_diff_data$diff_sd) / sqrt(nrow(hybrid_offset_diff_data))
```

This model combines the unisensory and multisensory models' predictions by weighting them according to their precisions [@Noppeney_2021]. The combined predicted uncertainity is lower than either individual model's prediction against target (@fig-model-hybrid-1) and is more sensitive to reliability around zero feedback offset (@fig-model-hybrid-2). Beyond the -60$^\circ$ to 60$^\circ$ feedback offset range, where uncertainity behaviorally plateaus, the hybrid model's predicted uncertainity is on average `r round(abs(hybrid_offset_diff_mean), 3)` $\pm$ `r round(2 * hybrid_offset_diff_se, 3)`$^\circ$ lower than the multisensory model's.

### Model Comparison

```{r}
#| label: fig-model-comparison
#| fig-cap: "**Median test NLL (across subjects) for the unisensory, naive multisensory, multisensory and hybrid models, faceted by signed feedback offset (conflict size)**"
#| code-summary: Compare models on held-out test NLL, by conflict size
#| code-fold: true
#| message: false
#| fig-width: 7
#| fig-height: 5

# Per-row held-out test-set NLL for a gamlss model fit with family SN2
test_nll_by_row <- function(model) {
  pred_mu <- suppressWarnings(predict(model, what = "mu", newdata = test, type = "response", data = train))
  pred_sigma <- suppressWarnings(predict(model, what = "sigma", newdata = test, type = "response", data = train))
  pred_nu <- suppressWarnings(predict(model, what = "nu", newdata = test, type = "response", data = train))
  -dSN2(test$error, mu = pred_mu, sigma = pred_sigma, nu = pred_nu, log = TRUE)
}

# Hybrid combines unisensory and multisensory sigma/nu via precision weighting, mu from multisensory
hybrid_test_nll_by_row <- {
  uni_sigma <- predict(unisensory, what = "sigma", newdata = test, type = "response", data = train)
  uni_nu <- predict(unisensory, what = "nu", newdata = test, type = "response", data = train)
  uni_sd <- sqrt(unisensory_family$variance(mu = 0, sigma = uni_sigma, nu = uni_nu))
  multi_mu <- suppressWarnings(predict(multisensory, what = "mu", newdata = test, type = "response", data = train))
  multi_sigma <- suppressWarnings(predict(multisensory, what = "sigma", newdata = test, type = "response", data = train))
  multi_nu <- suppressWarnings(predict(multisensory, what = "nu", newdata = test, type = "response", data = train))
  multi_sd <- sqrt(multisensory_family$variance(mu = 0, sigma = multi_sigma, nu = multi_nu))
  combined_sd <- sqrt(1 / (1 / uni_sd^2 + 1 / multi_sd^2))
  -dNO(test$error, mu = multi_mu, sigma = combined_sd, log = TRUE)
}

# 60 degree signed fb_offset bins, spanning the full range
conflict_bin_breaks <- seq(-180, 180, by = 60)
conflict_bin_labels <- paste(head(conflict_bin_breaks, -1), tail(conflict_bin_breaks, -1), sep = " to ")

# Per-trial NLL for each model on FB trials only, binned by signed fb_offset, summed per subject within each bin
model_comparison_by_conflict_subj <- tibble(
  subj = rep(test$subj, times = 4),
  condition = rep(test$condition, times = 4),
  fb_offset = rep(test$fb_offset, times = 4),
  Model = rep(c("Unisensory", "Naive Multisensory", "Multisensory", "Hybrid"), each = nrow(test)),
  nll = c(test_nll_by_row(unisensory), test_nll_by_row(naive_multisensory),
          test_nll_by_row(multisensory), hybrid_test_nll_by_row)
) %>%
  filter(condition == "FB") %>%
  mutate(conflict_bin = cut(fb_offset, breaks = conflict_bin_breaks, include.lowest = TRUE, labels = conflict_bin_labels),
         Model = factor(Model, levels = c("Unisensory", "Naive Multisensory", "Multisensory", "Hybrid"))) %>%
  group_by(subj, conflict_bin, Model) %>%
  summarise(nll = sum(nll), .groups = "drop")

# Median across subjects, per model per conflict bin
model_comparison_by_conflict <- model_comparison_by_conflict_subj %>%
  group_by(conflict_bin, Model) %>%
  summarise(median_nll = median(nll), .groups = "drop")

# Short model labels to keep the faceted x-axis readable
model_short_labels <- c("Unisensory" = "Uni", "Naive Multisensory" = "Naive", "Multisensory" = "Multi", "Hybrid" = "Hybrid")

# Plot NLL by model, faceted by conflict bin: per-subject lines with the across-subject median overlaid
model_comparison_plot <- model_comparison_by_conflict_subj %>%
  mutate(Model = factor(model_short_labels[Model], levels = model_short_labels)) %>%
  ggplot(aes(x = Model, y = nll)) +
  geom_point(aes(colour = subj)) +
  geom_line(aes(colour = subj, group = subj), alpha = 0.4) +
  geom_line(data = model_comparison_by_conflict %>% mutate(Model = factor(model_short_labels[Model], levels = model_short_labels)),
            aes(y = median_nll, group = 1), linewidth = 1) +
  geom_point(data = model_comparison_by_conflict %>% mutate(Model = factor(model_short_labels[Model], levels = model_short_labels)),
             aes(y = median_nll), size = 2.5) +
  facet_wrap(~ conflict_bin, nrow = 2, scales = "free_y") +
  scale_colour_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x = NULL, y = "Test NLL")

model_comparison_plot
```

The hybrid model has no BIC of its own since it is a precision-weighted combination of the already-fit unisensory and multisensory models rather than a separately fit likelihood. The multisensory model has both the lowest training BIC and the lowest median test NLL, making it the best-performing model overall. The hybrid model is compared alongside it in the behavioral validation below despite its higher test NLL, since precision-weighted cue combination is a theoretically motivated benchmark [@Noppeney_2021] rather than a model chosen purely for fit.

### Behavioral Validation

```{r}
#| label: behavioral-validation
#| code-summary: Validate multisensory and hybrid predictions against the behavioral relationships found for accuracy and confidence
#| code-fold: true
#| message: false

# Test trials with each model's predicted SD per trial
validation_test_data <- test %>%
  mutate(multi_sigma = suppressWarnings(predict(multisensory, what = "sigma", newdata = ., type = "response", data = train)),
         multi_nu = suppressWarnings(predict(multisensory, what = "nu", newdata = ., type = "response", data = train)),
         multisensory_pred_sd = sqrt(multisensory_family$variance(mu = 0, sigma = multi_sigma, nu = multi_nu)),
         uni_sigma = predict(unisensory, what = "sigma", newdata = ., type = "response", data = train),
         uni_nu = predict(unisensory, what = "nu", newdata = ., type = "response", data = train),
         uni_sd = sqrt(unisensory_family$variance(mu = 0, sigma = uni_sigma, nu = uni_nu)),
         hybrid_pred_sd = sqrt(1 / (1 / uni_sd^2 + 1 / multisensory_pred_sd^2)))

test_subjs <- unique(validation_test_data$subj)

# Bootstrapped median regression slopes of pred_sd_col ~ target and ~ |error| within the same resample,
# and their paired difference (target slope - |error| slope), each as a [lo, hi] CI
validation_slope_diff <- function(pred_sd_col, data) {
  b <- boot(test_subjs, function(d, i) {
    samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
    target_slope <- coef(rq(reformulate("target", response = pred_sd_col), tau = 0.5, data = samp))[[2]]
    error_slope <- coef(rq(reformulate("abs(error)", response = pred_sd_col), tau = 0.5, data = samp))[[2]]
    c(target = target_slope, error = error_slope, diff = target_slope - error_slope)
  }, R = R_boot)
  list(target = boot.ci(b, type = "perc", index = 1)$percent[4:5],
       error = boot.ci(b, type = "perc", index = 2)$percent[4:5],
       diff = boot.ci(b, type = "perc", index = 3)$percent[4:5])
}

multisensory_slopes <- validation_slope_diff("multisensory_pred_sd", validation_test_data)
hybrid_slopes <- validation_slope_diff("hybrid_pred_sd", validation_test_data)

# Format a [lo, hi] CI pair as a display string
format_ci <- function(ci) paste0("[", round(ci[1], 3), ", ", round(ci[2], 3), "]")

# The paired slope difference (target - |error|), computed per model on the test set
validation_results <- tibble(
  Model = c("Multisensory", "Hybrid"),
  `Slope difference (target - |error|)` = c(format_ci(multisensory_slopes$diff), format_ci(hybrid_slopes$diff))
)

validation_table <- validation_results %>%
  tableGrob(rows = NULL, theme = ttheme_default(base_size = 14))

grid.arrange(validation_table)
```

Uncertainity was expected to track task difficulty (`target`) rather than actual performance (`|error|`), matching the behavioral relationship found for subjective confidence. Both models' slope differences include 0, so neither model's predicted uncertainity is distinguishably more sensitive to task difficulty than to actual performance on the held-out test set, unlike subjective confidence. This is a limitation of both models.

### Bayes-Consistency Check

```{r}
#| label: bayes-consistency
#| code-summary: Check whether the hybrid model's implied vision weight shifts with feedback reliability
#| code-fold: true
#| message: false

# Implied precision-weight placed on the multisensory (vision-informed) estimate, all test trials
vision_weight_data <- validation_test_data %>%
  mutate(uni_precision = 1 / uni_sd^2,
         multi_precision = 1 / multisensory_pred_sd^2,
         vision_weight = multi_precision / (uni_precision + multi_precision))

# Bayes-optimal integration predicts this weight decreases as feedback becomes less reliable (|fb_offset| increases)
vision_weight_slope_boot <- boot(test_subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ vision_weight_data %>% filter(subj == .x))
  coef(rq(vision_weight ~ abs(fb_offset), tau = 0.5, data = samp))[["abs(fb_offset)"]]
}, R = R_boot)
vision_weight_slope_ci <- boot.ci(vision_weight_slope_boot, type = "perc")$percent[4:5]

# Does the slope of vision_weight ~ |fb_offset| change inside vs. outside the 60 degree band?
vision_weight_binned_data <- vision_weight_data %>%
  mutate(offset_bin = ifelse(abs(fb_offset) <= 60, "near_zero", "outside"))

vision_weight_bin_slope_boot <- boot(test_subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ vision_weight_binned_data %>% filter(subj == .x))
  near_slope <- coef(rq(vision_weight ~ abs(fb_offset), tau = 0.5, data = samp %>% filter(offset_bin == "near_zero")))[["abs(fb_offset)"]]
  outside_slope <- coef(rq(vision_weight ~ abs(fb_offset), tau = 0.5, data = samp %>% filter(offset_bin == "outside")))[["abs(fb_offset)"]]
  c(near = near_slope, outside = outside_slope, diff = near_slope - outside_slope)
}, R = R_boot)
vision_weight_near_ci <- boot.ci(vision_weight_bin_slope_boot, type = "perc", index = 1)$percent[4:5]
vision_weight_outside_ci <- boot.ci(vision_weight_bin_slope_boot, type = "perc", index = 2)$percent[4:5]
vision_weight_bin_diff_ci <- boot.ci(vision_weight_bin_slope_boot, type = "perc", index = 3)$percent[4:5]
```

Bayes-optimal cue integration predicts that the weight placed on the more reliable cue should increase as its reliability improves. The bootstrapped 95% CI for the median regression slope of the hybrid model's implied vision weight against `|fb_offset|` (unreliability) is [`r round(vision_weight_slope_ci[1], 4)`, `r round(vision_weight_slope_ci[2], 4)`]. Splitting at the 60$^\circ$ landmark seen earlier in the behavioral uncertainty plateau, the slope within the band is [`r round(vision_weight_near_ci[1], 4)`, `r round(vision_weight_near_ci[2], 4)`] and beyond it is [`r round(vision_weight_outside_ci[1], 4)`, `r round(vision_weight_outside_ci[2], 4)`], with a difference of [`r round(vision_weight_bin_diff_ci[1], 4)`, `r round(vision_weight_bin_diff_ci[2], 4)`].

