---
title: Undecided
engine: knitr
# format: gfm
from: markdown+wikilinks_title_after_pipe
link-citations: true
link-bibliography: true
execute:
  cache: true
---

[[Landscape/@Noppeney_2021/@Noppeney_2021|Multisensory processing]] occurs via integration across sensory modalities. But like any other system, our sensory apparatus adds noise to the incoming information. How are we able to perceive things so smoothly despite the uncertainty in the information received? Bayesian inference has been pegged as one of the possible mechanisms our brain uses to solve this intractable problem [@Noppeney_2021; @Kording_2007]. In addition to the noise generated by the sensory apparatus, the brain's computational resources are biologically constrained. Bayesian inference allows the internal processes in the brain to weigh the sensory information based on its reliability. Reliabilities provide a link between the internal model of the world and reality. Thus the weights are capturing the relationships which occur in the real world ie. the causal structure of the world around us. Integration of suboptimal information coming from different senses shows characteristics of normative (rule-based) bayesian framework [@Noppeney_2021]. One way to study this integration across modalities is to ask how does the brain differentiate if the information received is coming from common or independent sources ie. *the binding problem*. Spatial cognition is a prime example of the binding problem, especially in a naturalistic environment.
My main goal is to apply and confirm the mechanisms described in a multisensory integration review paper [@Noppeney_2021] to heading estimation task performed in VR [@Harootonian_2022].

## Experiment Design

33 participants wore VR headsets with controllers held in both hands in a rectangular room. Each participant performed ~400 trials for ~90 minutes. The sessions were divided into two blocks separated by a 2-10 minute break. The data from 3 participants is not present in the public dataset. These were excluded by the experimenters due to motion sickness.  

### Trial and Block Structure

Each trial followed the following structure:

- **Encoding period**: Participant faces a door on the VR screen. They rotate around the vertical axis towards the controller which vibrates in the right or left hand. The stop of the vibrations signals the participant has arrived to a *target* angular rotation.
- **Retrieval period**: The VR screen goes blank and the participant is asked to rotate back to re-face the door. The direction choice for turning back was left to the participants. There were two types of retrieval periods:
    - *noFb* trials: No visual feedback is provided
    - *FB* trials: ~ 300 msec flash of the virtual environment is provided as feedback while they are turning back to re-face the door
- **Response period**: Participants press a button on the controller to record their response. No time limits were set.
- **Subjective rating period**: Paticipants adjust a red triangle's angle to indicate their confidence.

Each of the two blocks were divided into:

- **Practice period**: 10 trials
- **No Feedback period**: 25 trials
- **Feedback period**: 150 trials
- **No Feedback period**: 25 trials

### Ethological significance

The trial structure reminded me of when I would enter a room, grab something and leave through the door all the while focusing on my phone. Humans are able to perform this simple task with great fidelity even in novel environments. The immersive nature of the VR, free-choice for direction during the retrieval period and no time limits add to the ethological relevance of the experiment. The subjective rating period provides a reset time for the participants and may reduce the effects due to learning. Can adding a response action of opening the door in the virtual environment increase the ethological relevance?  

## Data Structure

```{r}
#| label: imports
#| code-summary: Imports
#| code-fold: true
#| message: false
# Import necessary libraries
library(here)
library(tidyverse)
library(tidymodels)
library(circular)
library(gridExtra)
library(boot)
library(quantreg)
library(rmcorr)

# Pin the here() root explicitly
here::i_am("scripts/heading-estimation-multisensory-proc.qmd")
```

```{r}
#| label: download-data
#| code-summary: Download data
#| code-fold: true
# Get the data path
data_path <- here("data")
# Make the directory if it does not exist already
dir.create(data_path, recursive = TRUE, showWarnings = FALSE)
# Download dataconf.csv to data_path if not already present
if (!file.exists(file.path(data_path, "dataconf.csv"))) {
  dataconf_url <- "https://raw.githubusercontent.com/sharootonian/CombinationAndCompetitionHeadingDirection/main/data/dataconf.csv"
  download.file(dataconf_url, file.path(data_path, "dataconf.csv"), mode = "wb")
}
```

```{r}
#| label: preprocess-data
#| code-summary: Load, preprocess and split data into train, validation and test splits
#| code-fold: true
#| message: false

# Load data
dataconf <- read_csv(file.path(data_path, "dataconf.csv"))

# Prepare the data for train, validation and test splits
data <- dataconf %>%
  # Convert the subject column into a factor
  mutate(subj = factor(as.integer(str_remove(subj, "^s")))) %>%
  # Convert the condition column into a factor
  mutate(condition = factor(condition, levels = c("noFB", "FB"))) %>%
  # Since feedback validity labels are not present, use label reliable for gaussian (0, 30) +/- 3SD
  mutate(fb_validity = factor(case_when(condition == "noFB" ~ NA,
                                        abs(fb_offset) <= 90 ~ "reliable",
                                        TRUE ~ "unreliable"),
                              levels = c("reliable", "unreliable"))) %>%
  # Create a new column to signify the three trial types
  mutate(trial_type = if_else(condition == "noFB", "noFB", as.character(fb_validity))) %>%
  mutate(trial_type = factor(trial_type, levels = c("noFB", "reliable", "unreliable")))

# Split into train (70%), validation (15%) and test (15%) by whole subjects
set.seed(246) # For reproducibility
data_split <- group_initial_split(data, group = subj, prop = 0.7)
train <- training(data_split)
remainder <- testing(data_split)

# Split the remainder evenly into validation and test by whole subjects
remainder_split <- group_initial_split(remainder, group = subj, prop = 0.5)
validation <- training(remainder_split)
test <- testing(remainder_split)
```

`dataconf.csv` contains the following columns:

- *subj*: Participant identifier; `r length(unique(data$subj))` participants in total
- *trial*: Trial identifier; some trials were excluded from the data when the participant rotated in the wrong direction during encoding period, pressed the wrong response button or responded before receiving the visual feedback
- *target* (degrees): Angle value where the controller vibration stops ranging from `0` to `360`; circularly uniform and anchored to the door
- *respond* (degrees): Total angle the participant turns during the retrieval period ie. accumulates before the response
- *error* (degrees): `respond` - `target`; objective measure of performance
- *condition*: Marks `FB` vs. `noFB` trials
- *fb* (degrees): Angular position of the feedback shown; anchored to the door
- *fb_true* (degrees): True angular position of the feedback; anchored to the door
- *fb_offset* (degrees): `fb` - `fb_true`; signifies the reliability of the visual feedback. These were generated in two ways:
    - 70% of the trials: $\sim Gaussian(0, 30)$
    - 30% of the trials: $\sim Uniform(-180, 180)$
- *fb_time* (msec): Marks the time from trial start to feedback flash
- *trial_duration* (msec): Total time taken by the participant to press the response button from trial start
- *conf* (degrees): Response confidence level; subjective measure of performance
- *viewAmount* (degrees): View angle traversed by the participant while the visual feedback was visible; signifies how much attention was payed to the feedback. For eg., a lower `viewAmount` would suggest that the participant slowed down to reorient themselves to the new context obtained from the feedback

## Analysis (think of a descriptive title)

### Stimulus Design

```{r}
#| label: fig-stimulus-design
#| fig-cap: "**Distributions of target heading and visual feedback offset across participants**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Confirm almost similar concentration of target angles is present across each subject
rho_by_subj <- train %>%
  summarise(rho = rho.circular(circular(target, units = "degrees")), .by = subj)
# Find the mean and sd of the concentration of target angles
rho_mean <- mean(rho_by_subj$rho)
rho_sd <- sd(rho_by_subj$rho)

# Define the 20 degree target bins for plotting purposes
target_bin_breaks <- seq(0, 360, by = 20)
target_bin_labels <- paste(head(target_bin_breaks, -1), tail(target_bin_breaks, -1), sep = "-")
target_bins <- cut(
  train$target, breaks = target_bin_breaks,
  include.lowest = TRUE, labels = target_bin_labels
)

# Show every 3rd bin label for even, uncluttered spacing
target_bin_ticks <- target_bin_labels[seq(1, length(target_bin_labels), by = 3)]

# Display distribution of target headings
plot_target <- train %>%
  # Divide target into 20 degree bins, dropping subj levels absent from train
  mutate(target_bin = target_bins, subj = factor(subj)) %>%
  count(subj, target_bin, .drop = FALSE) %>%
  # Summarize by subjects to confirm consistency
  group_by(subj) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  summarise(mean_prop = mean(prop), sd_prop = sd(prop), .by = target_bin) %>%
  ggplot(aes(x = target_bin, y = mean_prop)) +
  geom_col(colour = "steelblue", fill = "steelblue") +
  geom_errorbar(
    aes(ymin = mean_prop - sd_prop, ymax = mean_prop + sd_prop),
    width = 0.2
  ) +
  # Change to a circular coordinate
  coord_polar(start = 0) +
  labs(
    x = expression(paste("target heading (", degree, ")")),
    y = "proportion of trials"
  ) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 9)
  )

# Confirm the ~70/30 split matches the original design for all participants
reliabililty_by_subj <- train %>%
  filter(condition == "FB") %>%
  summarise(prop_reliable = mean(abs(fb_offset) <= 90), .by = subj)
# Find the mean and sd of reliable trials across subjects
reliability_mean <- mean(reliabililty_by_subj$prop_reliable)
reliability_sd <- sd(reliabililty_by_subj$prop_reliable)

# Display distribution of fb_offset which was drawn from two components
breaks <- seq(-180, 180, by = 20)
bin_width <- 20
centers <- breaks[-length(breaks)] + bin_width / 2

fb_agg <- train %>%
  filter(condition == "FB") %>%
  mutate(
    bin_center = centers[cut(fb_offset, breaks = breaks, include.lowest = TRUE, labels = FALSE)],
    subj = factor(subj)
  ) %>%
  count(subj, bin_center, .drop = FALSE) %>%
  # Summarize by subjects to confirm consistency
  group_by(subj) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  summarise(mean_prop = mean(prop), se_prop = sd(prop) / sqrt(n()), .by = bin_center)

# Source distributions
theo_gaussian <- function(x) 0.7 * dnorm(x, 0, 30) * bin_width
theo_uniform  <- function(x) 0.3 * dunif(x, -180, 180) * bin_width

# Build the plot
plot_fb_offset <- ggplot(fb_agg, aes(x = bin_center, y = mean_prop)) +
  geom_col(width = bin_width * 0.9, fill = "grey70") +
  geom_errorbar(aes(ymin = mean_prop - se_prop, ymax = mean_prop + se_prop), width = bin_width * 0.2) +
  geom_function(aes(color = "~ Gaussian(0, 30)"), fun = theo_gaussian, xlim = c(-180, 180), linewidth = 1) +
  geom_function(aes(color = "~ Uniform(-180, 180)"), fun = theo_uniform, xlim = c(-180, 180), linewidth = 1) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Visual feedback offset", y = "proportion of FB trials", color = NULL) +
  theme_classic() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.position = "inside", legend.position.inside = c(1, 1),
    legend.justification = c(1, 1),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1.2, "lines")
  )

plot_target
plot_fb_offset
```

- Target headings are widely spread for all subjects (circular $\rho$ = `r round(rho_mean, 2)` $\pm$ `r 2*round(rho_sd, 2)`) (@fig-stimulus-design-1). The most likely explanation for this design decision might be to prevent formation of any pattern matching habits in the participants.
- Visual feedback offset distribution resembles a gaussian in the range of $0^\circ \pm 3 \times 30^\circ$ and uniform beyond that (@fig-stimulus-design-2). For illustration purposes only, the reliability of the visual feedback is tracked. Any trial with the offset falling in the above range is marked as reliable to approximate the reliability from the participant's viewpoint. This resulted in `r round(reliability_mean, 4)*100`% $\pm$ `r 2*round(reliability_sd, 4)*100`% marked as reliable.

### Response Characteristics

```{r}
#| label: fig-respond-error-by-target
#| fig-cap: "**Mean respond and median error across target heading bins**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Define the number of bootstraps
R_boot <- 1000

# Compute the mean of respond per target bins
respond_boot_by_bin <- train %>%
  mutate(target_bin = target_bins, include.lowest = TRUE) %>%
  group_by(target_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      mean(samp$respond)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(mean = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for respond vs. target
plot_A <- ggplot(respond_boot_by_bin, aes(x = target_bin, y = mean)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "Mean(respond) with 95% bootstrap CI")

# Compute the median of error per target bins
error_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error vs. target
plot_B <- ggplot(error_boot_by_bin, aes(x = target_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "Median(error) with 95% bootstrap CI")

plot_A
plot_B

# Is error truly positively biased?
error_wilcox <- wilcox.test(train$error, mu = 0)
subjs <- unique(train$subj)
median_error_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  median(samp$error)
}, R = R_boot)
median_error_ci <- boot.ci(median_error_boot, type = "perc")$percent[4:5]

# Does error stay constant (flat trend) across target?
# Controlling for individual subjects
error_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(error ~ target, tau = 0.5, data = samp))["target"]
}, R = R_boot)
error_slope_ci <- boot.ci(error_slope_boot, type = "perc")$percent[4:5]

# Is respond's variance coming directly from error rather than target?
# ie. check if the last term in Var(respond) = var(target) + var(error) + 2 cov(target, error) -> 0
# Repeated measures correlation controls for subject to avoid pooling across subjects
respond_error_rmcorr <- rmcorr(subj, target, error, dataset = train)
```

- Respond angle increases monotonically with target, consistent with `respond` = `target` + `error` relationship (@fig-respond-error-by-target-1). The width of the bootstrapped (`1000`) 95% confidence interval (CI) also increases with target angle suggesting an increase in uncertainity with increasing difficulty of the task.
- Median error is consistently positive (Wilcoxon signed-rank test, `r ifelse(error_wilcox$p.value < 0.001, "p < 0.001", paste("p =", round(error_wilcox$p.value, 3)))`; bootstrapped median 95% CI [`r round(median_error_ci[1], 2)`, `r round(median_error_ci[2], 2)`]) but does not increase or decrease as a function of target angle (bootstrapped median regression slope 95% CI [`r round(error_slope_ci[1], 3)`, `r round(error_slope_ci[2], 3)`]). However, the width of the bootstrapped (`1000`) 95% CI for mean error increases with target angle just like respond (@fig-respond-error-by-target-2).
- The growing uncertainty in `respond` tracks `error` directly, since:

$$
\begin{aligned}
&respond = target + error \\
\implies &Var(respond) = Var(target) + Var(error) + 2\;Cov(target, error)
\end{aligned}
$$

  The repeated measures correlation between `target` and `error` is negligible ($r$ = `r round(respond_error_rmcorr$r, 3)`, 95% CI [`r round(respond_error_rmcorr$CI[1], 3)`, `r round(respond_error_rmcorr$CI[2], 3)`]). Thus, `error` can be used as the predicting variable instead of `respond` to model participant's response.

```{r}
#| label: fig-error-by-condition-offset
#| fig-cap: "**Median error by condition and by visual feedback offset magnitude**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Compute the median error per condition
condition_median_boot <- train %>%
  group_by(condition) %>%
  group_modify(~ {
    group_data <- .x
    group_subjs <- unique(group_data$subj)
    b <- boot(group_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ group_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error vs. condition
plot_C <- ggplot(condition_median_boot, aes(x = condition, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(labels = c(noFB = "No Feedback", FB = "Feedback")) +
  theme_classic() +
  labs(x = "Condition", y = "Median(error) with 95% bootstrap CI")

# Define the 20 degree |fb_offset| bins for plotting purposes, FB trials only
fb_data <- train %>%
  filter(condition == "FB") %>%
  mutate(abs_offset = abs(fb_offset))
offset_bin_breaks <- seq(0, 180, by = 20)
offset_bin_labels <- paste(head(offset_bin_breaks, -1), tail(offset_bin_breaks, -1), sep = "-")
offset_bins <- cut(
  fb_data$abs_offset, breaks = offset_bin_breaks,
  include.lowest = TRUE, labels = offset_bin_labels
)

# Compute the median error per |fb_offset| bin
offset_median_boot_by_bin <- fb_data %>%
  mutate(offset_bin = offset_bins) %>%
  group_by(offset_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error vs. |fb_offset|
plot_D <- ggplot(offset_median_boot_by_bin, aes(x = offset_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Visual feedback offset magnitude", y = "Median(error) with 95% bootstrap CI")

plot_C
plot_D

# Does error's median differ between noFB and FB conditions?
# Controlled for subjects
condition_median_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  median(samp$error[samp$condition == "FB"]) - median(samp$error[samp$condition == "noFB"])
}, R = R_boot)
condition_median_diff_ci <- boot.ci(condition_median_diff_boot, type = "perc")$percent[4:5]

# Does error's median grow with the magnitude of fb_offset?
# Controlled for subjects
offset_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ fb_data %>% filter(subj == .x))
  coef(rq(error ~ abs_offset, tau = 0.5, data = samp))["abs_offset"]
}, R = R_boot)
offset_slope_ci <- boot.ci(offset_slope_boot, type = "perc")$percent[4:5]
```

- Median error was higher in trials where visual feedback was provided (bootstrapped 95% CI of difference between two conditions = [`r round(condition_median_diff_ci[1], 2)`, `r round(condition_median_diff_ci[2], 2)`]), consistent with varying reliability of the visual feedback (@fig-error-by-condition-offset-1). The above deviation from the forced fusion model based on a normative Bayesian observer has been shown before where the observers have a tendency to overweight signals from a sensory modality (vision) which can provide better information than their own proprioceptive sense [@Noppeney_2021].
- But the median error does not increase monotonically with offset magnitude (bootstrapped 95% CI for median regression slope [`r round(offset_slope_ci[1], 3)`, `r round(offset_slope_ci[2], 3)`]) (@fig-error-by-condition-offset-2). The reliability of the cue itself is taken into consideration beyond a certain limit (around 60$^\circ$ in this case). The extent of integration between proprioception and vision depends more on the size of the conflict between the information from both sources and less on the uncertainity of the information itself [@Noppeney_2021].

```{r}
#| label: fig-error-variance
#| fig-cap: "**SD of error across target heading bins, condition, and visual feedback offset magnitude**"
#| fig-subcap: true
#| layout-ncol: 3
#| code-summary: ""
#| code-fold: true
#| fig-width: 4
#| fig-height: 5

# Does the variance of error grow across target bins?
# Controlling for individual subjects
error_sd_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error's SD vs. target
plot_E <- ggplot(error_sd_boot_by_bin, aes(x = target_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "SD(error) with 95% bootstrap CI")

# Does error's SD differ between noFB and FB conditions?
# Controlled for subjects
condition_sd_boot <- train %>%
  group_by(condition) %>%
  group_modify(~ {
    group_data <- .x
    group_subjs <- unique(group_data$subj)
    b <- boot(group_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ group_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error's SD vs. condition
plot_F <- ggplot(condition_sd_boot, aes(x = condition, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(labels = c(noFB = "No Feedback", FB = "Feedback")) +
  theme_classic() +
  labs(x = "Condition", y = "SD(error) with 95% bootstrap CI")

# Does error's SD grow with the magnitude of fb_offset?
# Controlled for subjects
offset_sd_boot_by_bin <- fb_data %>%
  mutate(offset_bin = offset_bins) %>%
  group_by(offset_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for error's SD vs. |fb_offset|
plot_G <- ggplot(offset_sd_boot_by_bin, aes(x = offset_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Visual feedback offset magnitude", y = "SD(error) with 95% bootstrap CI")

plot_E
plot_F
plot_G

# Does error's SD differ between noFB and FB conditions? (magnitude of the difference)
# Controlled for subjects
condition_sd_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  sd(samp$error[samp$condition == "FB"]) - sd(samp$error[samp$condition == "noFB"])
}, R = R_boot)
condition_sd_diff_ci <- boot.ci(condition_sd_diff_boot, type = "perc")$percent[4:5]

# Does |error| (1/accuracy) change with viewAmount (attention paid to the feedback cue)?
# FB trials only; controlled for subjects
accuracy_view_amount_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ fb_data %>% filter(subj == .x))
  coef(rq(abs(error) ~ viewAmount, tau = 0.5, data = samp))["viewAmount"]
}, R = R_boot)
accuracy_view_amount_slope_ci <- boot.ci(accuracy_view_amount_slope_boot, type = "perc")$percent[4:5]
```

- Standard deviation (SD) of error maybe a measure of uncertainity about the information. As @fig-error-variance-1 shows, SD of error grows with task difficulty, but it rises in two phases separated by a plateau in the range of 120$^\circ$ to 240$^\circ$.
- The amount of uncertainity was higher in trials where visual feedback was provided (bootstrapped 95% CI of difference = [`r round(condition_sd_diff_ci[1], 2)`, `r round(condition_sd_diff_ci[2], 2)`]) (@fig-error-variance-2).
- The amount of uncertainity rises with unreliability of the visual feedback but then plateaus around 60$^\circ$ (@fig-error-variance-3). The internal model might be tracking the reliability of the visual feedback reinforcing the impact of conflict size on integration of visual and proprioceptive information.

From the above characteristics of the participants' responses, it is clear that the magnitude of error depends on both the proprioceptive and visual information. The final perceptual estimate is computed by averaging the individual estimates weighted by their reliabilities [@Noppeney_2021], but this may or may not happen in a normative manner depending on the size of the conflict between the two information sources.

Accuracy (1/|`error`|) improves as attention increases (`viewAmount` decreases) (bootstrapped 95% CI for the median regression slope [`r round(accuracy_view_amount_slope_ci[1], 3)`, `r round(accuracy_view_amount_slope_ci[2], 3)`]). The accuracy of the best model will be validated against this behavioral characteritic.

### Subjective Measure (make it more descriptive)

```{r}
#| label: fig-conf-by-target
#| fig-cap: "**Median and SD of subjective confidence across target heading bins**"
#| fig-subcap: true
#| layout-ncol: 2
#| code-summary: ""
#| code-fold: true
#| fig-width: 5
#| fig-height: 6

# Compute the median of conf per target bins
conf_median_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$conf)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for conf vs. target
plot_H <- ggplot(conf_median_boot_by_bin, aes(x = target_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "Median(conf) with 95% bootstrap CI")

# Does subjective confidence (conf) grow with target (task difficulty)?
# Controlled for subjects
conf_target_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(conf ~ target, tau = 0.5, data = samp))["target"]
}, R = R_boot)
conf_target_slope_ci <- boot.ci(conf_target_slope_boot, type = "perc")$percent[4:5]

# Does conf's SD also grow with target?
# Controlling for individual subjects
conf_sd_boot_by_bin <- train %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$conf)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })
# Define the plot for conf's SD vs. target
plot_I <- ggplot(conf_sd_boot_by_bin, aes(x = target_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Target Heading", y = "SD(conf) with 95% bootstrap CI")

plot_H
plot_I

# Does conf track |error| ie. 1/accuracy?
# Controlled for subjects
conf_error_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ train %>% filter(subj == .x))
  coef(rq(conf ~ abs(error), tau = 0.5, data = samp))["abs(error)"]
}, R = R_boot)
conf_error_slope_ci <- boot.ci(conf_error_slope_boot, type = "perc")$percent[4:5]
```

- Subjective confidence reduces with task difficulty (bootstrapped 95% CI for the median regression slope [`r round(conf_target_slope_ci[1], 3)`, `r round(conf_target_slope_ci[2], 3)`]) similar to error which is an objective measure of performance (@fig-conf-by-target-1).
- But SD of this subjective measure does not grow with task difficulty (@fig-conf-by-target-2).
- Confidence does not track performance accuracy (1/|`error`|) (bootstrapped 95% CI for the median regression slope [`r round(conf_error_slope_ci[1], 3)`, `r round(conf_error_slope_ci[2], 3)`]).

Thus, participants track their performance based on the task's difficulty and not on how well they actually did. The winning model's internal uncertainity measure will be validated against these behavioral characteristics.  

