---
title: Beyond Cue Combination for Multisensory Heading Estimation in VR
engine: knitr
format: gfm
from: markdown+wikilinks_title_after_pipe
bibliography: heading-estimation-multisensory-proc.bib
link-citations: true
link-bibliography: true
execute:
  cache: true
---

[[Landscape/@Noppeney_2021/@Noppeney_2021|Multisensory processing]] occurs via integration across sensory modalities. But like any other system, our sensory apparatus adds noise to the incoming information. How are we able to perceive things so smoothly despite the uncertainty in the information received? Bayesian inference has been pegged as one of the possible mechanisms our brain uses to solve this intractable problem [@Noppeney_2021; @Kording_2007]. In addition to the noise generated by the sensory apparatus, the brain's computational resources are biologically constrained. Bayesian inference allows the internal processes in the brain to weigh the sensory information based on its reliability. Reliabilities provide a link between the internal model of the world and reality. The weights capture the relationships which occur in the real world ie. the causal structure of the world around us. Integration of suboptimal information coming from different senses shows characteristics of a normative (rule-based) Bayesian framework [@Noppeney_2021]. One way to study this integration across modalities is to ask how the brain differentiates whether the information received is coming from common or independent sources ie. *the binding problem*. Spatial cognition is a prime example of the binding problem, especially in a naturalistic environment.
My main goal is to apply and confirm the mechanisms described in a multisensory integration review paper [@Noppeney_2021] to a heading estimation task performed in VR [@Harootonian_2022].

## Experiment Design

33 participants wore VR headsets with controllers held in both hands in a rectangular room. Each participant performed ~400 trials for ~90 minutes. The sessions were divided into two blocks separated by a 2-10 minute break. The data from 3 participants were excluded by the experimenters due to motion sickness.

### Trial and Block Structure

Each trial followed the following structure:

- **Encoding period**: Participant faces a door on the VR screen. They rotate around the vertical axis towards the controller which vibrates in the right or left hand. Participants are instructed to stop rotating when the vibrations stop indicating *target* angular rotation.
- **Retrieval period**: The VR screen goes dark and the participant is asked to rotate back to re-face the door. The direction choice for turning back was left to the participants. There were two types of retrieval periods:
    - *noFb* trials: No visual feedback is provided
    - *FB* trials: ~ 300 msec flash of the virtual environment is provided as feedback while they are turning back to re-face the door
- **Response period**: Participants press a button on the controller to record their response once they think they are facing the virtual door. No time limits were set.
- **Subjective rating period**: Participants adjust a red triangle's angle to indicate their confidence.

Each of the two blocks was divided into:

- **Practice period**: 10 trials
- **No Feedback period**: 25 trials
- **Feedback period**: 150 trials
- **No Feedback period**: 25 trials

### Ethological significance

The trial structure reminded me of when I would enter a room, grab something and leave through the door all the while focusing on my phone. Humans are able to perform this simple task with great fidelity even in novel environments. The immersive nature of the VR, free-choice for direction during the retrieval period and no time limits add to the ethological relevance of the experiment. The subjective rating period provides a reset time for the participants and may reduce the effects due to learning. Can adding a response action of opening the door in the virtual environment increase the ethological relevance?  

## Data Structure

```{r}
#| label: imports
#| code-summary: Imports
#| code-fold: true
#| message: false
# Import necessary libraries
library(here)
library(tidyverse)
library(circular)
library(boot)
library(quantreg)
library(rmcorr)
library(gamlss)
library(lemon)
library(patchwork)
library(gt)

# Pin the here() root explicitly
here::i_am("scripts/heading-estimation-multisensory-proc.qmd")

# Custom theme for tables
dark_header_gt <- function(data, size = 20) {
  data %>%
    gt() %>%
    tab_style(style = cell_fill(color = "grey30"), locations = cells_column_labels()) %>%
    tab_style(style = cell_text(color = "white", weight = "bold"), locations = cells_column_labels()) %>%
    cols_align(align = "left", columns = 1) %>%
    cols_align(align = "center", columns = -1) %>%
    tab_options(
      table.font.size = size,
      column_labels.border.top.width = 0,
      table_body.hlines.width = 0,
      table.border.top.width = 0,
      table.border.bottom.width = 0
    )
}
```

```{r}
#| label: download-data
#| code-summary: Download data
#| code-fold: true
# Get the data path
data_path <- here("data")
# Make the directory if it does not exist already
dir.create(data_path, recursive = TRUE, showWarnings = FALSE)
# Download dataconf.csv to data_path if not already present
if (!file.exists(file.path(data_path, "dataconf.csv"))) {
  dataconf_url <- "https://raw.githubusercontent.com/sharootonian/CombinationAndCompetitionHeadingDirection/main/data/dataconf.csv"
  download.file(dataconf_url, file.path(data_path, "dataconf.csv"), mode = "wb")
}
```

```{r}
#| label: preprocess-data
#| code-summary: Load and preprocess data
#| code-fold: true
#| message: false

# Load data
dataconf <- read_csv(file.path(data_path, "dataconf.csv"))

# Prepare the data
data <- dataconf %>%
  # Convert the subject column into a factor
  mutate(subj = factor(as.integer(str_remove(subj, "^s")))) %>%
  # Convert the condition column into a factor
  mutate(condition = factor(condition, levels = c("noFB", "FB")))
```

`dataconf.csv` contains the following columns:

- *subj*: Participant identifier; `r length(unique(data$subj))` participants in total
- *trial*: Trial identifier; some trials when the participant rotated in the wrong direction during encoding period, pressed the wrong response button or responded before receiving the visual feedback were excluded by the experimenters
- *target* (degrees): Angle value at which the controller vibration stops ranging from `0` to `360`; circularly uniform and anchored to the door
- *respond* (degrees): Total angle the participant turns during the retrieval period ie. the angle accumulated before the response
- *error* (degrees): `respond` - `target`; objective measure of performance
- *condition*: Marks `FB` vs. `noFB` trials
- *fb* (degrees): Angular position of the feedback shown; anchored to the door
- *fb_true* (degrees): True angular position of the feedback; anchored to the door
- *fb_offset* (degrees): `fb` - `fb_true`; signifies the reliability of the visual feedback. These were generated in two ways:
    - 70% of the trials: $\sim Gaussian(0, 30)$
    - 30% of the trials: $\sim Uniform(-180, 180)$
- *fb_time* (msec): Marks the time from trial start to feedback flash
- *trial_duration* (msec): Total time taken by the participant to press the response button from trial start
- *conf* (degrees): Response confidence level; subjective measure of performance
- *viewAmount* (degrees): View angle traversed by the participant while the visual feedback was visible; signifies how much attention was paid to the feedback. For example, a lower `viewAmount` would suggest that the participant slowed down to reorient themselves to the new context obtained from the feedback

## Behavioral Characteristics

Every bootstrap check below draws `1000` resamples of across subjects rather than individual trials, so no subject's data leaks into another's resample.

### Stimulus Design

```{r}
#| code-summary: ""
#| code-fold: true

# Confirm almost similar concentration of target angles is present across each subject
rho_by_subj <- data %>%
  summarise(rho = rho.circular(circular(target, units = "degrees")), .by = subj)
# Find the mean and sd of the concentration of target angles
rho_mean <- mean(rho_by_subj$rho)
rho_sd <- sd(rho_by_subj$rho)

# Define the 20 degree target bins for plotting purposes
target_bin_breaks <- seq(0, 360, by = 20)
target_bin_labels <- paste(head(target_bin_breaks, -1), tail(target_bin_breaks, -1), sep = "-")
target_bins <- cut(
  data$target, breaks = target_bin_breaks,
  include.lowest = TRUE, labels = target_bin_labels
)

# Show every 3rd bin label for even, uncluttered spacing
target_bin_ticks <- target_bin_labels[seq(1, length(target_bin_labels), by = 3)]

# Display distribution of fb_offset which was drawn from two components
breaks <- seq(-180, 180, by = 20)
bin_width <- 20
centers <- breaks[-length(breaks)] + bin_width / 2

fb_agg <- data %>%
  filter(condition == "FB") %>%
  mutate(
    bin_center = centers[cut(fb_offset, breaks = breaks, include.lowest = TRUE, labels = FALSE)],
    subj = factor(subj)
  ) %>%
  count(subj, bin_center, .drop = FALSE) %>%
  # Summarize by subjects to confirm consistency
  group_by(subj) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  summarise(mean_prop = mean(prop), se_prop = sd(prop) / sqrt(n()), .by = bin_center)
```

```{r}
#| label: fig-stimulus-design
#| fig-cap: "**Distributions of target heading and visual feedback offset across participants**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 10
#| fig-height: 6

# Display distribution of target headings
plot_target <- data %>%
  # Divide target into 20 degree bins, dropping subj levels absent from data
  mutate(target_bin = target_bins, subj = factor(subj)) %>%
  count(subj, target_bin, .drop = FALSE) %>%
  # Summarize by subjects to confirm consistency
  group_by(subj) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  summarise(mean_prop = mean(prop), sd_prop = sd(prop), .by = target_bin) %>%
  ggplot(aes(x = target_bin, y = mean_prop)) +
  geom_col(colour = "steelblue", fill = "steelblue") +
  geom_errorbar(
    aes(ymin = mean_prop - sd_prop, ymax = mean_prop + sd_prop),
    width = 0.2
  ) +
  # Change to a circular coordinate
  coord_polar(start = 0) +
  labs(
    x = expression(paste("target heading (", degree, ")")),
    y = "proportion of trials"
  ) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

# Source distributions
theo_gaussian <- function(x) 0.7 * dnorm(x, 0, 30) * bin_width
theo_uniform  <- function(x) 0.3 * dunif(x, -180, 180) * bin_width

# Build the plot
plot_fb_offset <- ggplot(fb_agg, aes(x = bin_center, y = mean_prop)) +
  geom_col(width = bin_width * 0.9, fill = "grey70") +
  geom_errorbar(aes(ymin = mean_prop - se_prop, ymax = mean_prop + se_prop), width = bin_width * 0.2) +
  geom_function(aes(color = "~ Gaussian(0, 30)"), fun = theo_gaussian, xlim = c(-180, 180), linewidth = 1) +
  geom_function(aes(color = "~ Uniform(-180, 180)"), fun = theo_uniform, xlim = c(-180, 180), linewidth = 1) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Visual feedback offset", y = "proportion of FB trials", color = NULL) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.position = "inside", legend.position.inside = c(1, 1),
    legend.justification = c(1, 1),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1.2, "lines")
  )

(plot_target | plot_fb_offset) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Target headings are widely spread for all subjects (circular $\rho$ = `r round(rho_mean, 2)` $\pm$ `r 2*round(rho_sd, 2)`) (@fig-stimulus-design(a)). The most likely explanation for this design decision might be to prevent formation of any pattern matching habits in the participants.
- Visual feedback offset distribution resembles a Gaussian in the range of $0^\circ \pm 3 \times 30^\circ$ and uniform beyond that (@fig-stimulus-design(b)), consistent with how the offsets were generated.

### Response Characteristics

```{r}
#| code-summary: ""
#| code-fold: true

# Define the number of bootstraps
R_boot <- 1000

# Compute the mean of respond per target bins
respond_boot_by_bin <- data %>%
  mutate(target_bin = target_bins, include.lowest = TRUE) %>%
  group_by(target_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      mean(samp$respond)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(mean = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Compute the median of error per target bins
error_boot_by_bin <- data %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Is error truly positively biased?
error_wilcox <- wilcox.test(data$error, mu = 0)
subjs <- unique(data$subj)
median_error_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  median(samp$error)
}, R = R_boot)
median_error_ci <- boot.ci(median_error_boot, type = "perc")$percent[4:5]

# Does error stay constant (flat trend) across target?
# Controlling for individual subjects
error_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  coef(rq(error ~ target, tau = 0.5, data = samp))["target"]
}, R = R_boot)
error_slope_ci <- boot.ci(error_slope_boot, type = "perc")$percent[4:5]

# Is respond's variance coming directly from error rather than target?
# ie. check if the last term in Var(respond) = var(target) + var(error) + 2 cov(target, error) -> 0
# Repeated measures correlation controls for subject to avoid pooling across subjects
respond_error_rmcorr <- rmcorr(subj, target, error, dataset = data)
```

```{r}
#| label: fig-respond-error-by-target
#| fig-cap: "**Mean respond and median error across target heading bins**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 10
#| fig-height: 6

# Define the plot for respond vs. target
plot_A <- ggplot(respond_boot_by_bin, aes(x = target_bin, y = mean)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Target Heading", y = "Mean(respond) with 95% bootstrap CI")

# Define the plot for error vs. target
plot_B <- ggplot(error_boot_by_bin, aes(x = target_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Target Heading", y = "Median(error) with 95% bootstrap CI")

(plot_A | plot_B) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Respond angle increases monotonically with target, consistent with `respond` = `target` + `error` relationship (@fig-respond-error-by-target(a)). The width of the bootstrapped 95% confidence interval (CI) also increases with target angle suggesting an increase in uncertainty with increasing difficulty of the task.
- Median error is consistently positive (Wilcoxon signed-rank test, `r ifelse(error_wilcox$p.value < 0.001, "p < 0.001", paste("p =", round(error_wilcox$p.value, 3)))`; bootstrapped median 95% CI [`r round(median_error_ci[1], 2)`, `r round(median_error_ci[2], 2)`]) but does not increase or decrease as a function of target angle (bootstrapped median regression slope 95% CI [`r round(error_slope_ci[1], 3)`, `r round(error_slope_ci[2], 3)`]). However, the width of the bootstrapped 95% CI for mean error increases with target angle just like respond (@fig-respond-error-by-target(b)).
- The growing uncertainty in `respond` tracks `error` directly, since:

$$
\begin{aligned}
&respond = target + error \\
\implies &Var(respond) = Var(target) + Var(error) + 2\;Cov(target, error)
\end{aligned}
$$

  The repeated measures correlation between `target` and `error` is negligible ($r$ = `r round(respond_error_rmcorr$r, 3)`, 95% CI [`r round(respond_error_rmcorr$CI[1], 3)`, `r round(respond_error_rmcorr$CI[2], 3)`]). Thus, `error` can be used as the predicting variable instead of `respond` to model a participant's response.

```{r}
#| code-summary: ""
#| code-fold: true

# Compute the median error per condition
condition_median_boot <- data %>%
  group_by(condition) %>%
  group_modify(~ {
    group_data <- .x
    group_subjs <- unique(group_data$subj)
    b <- boot(group_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ group_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Define the 20 degree signed fb_offset bins for plotting purposes
fb_data <- data %>%
  filter(condition == "FB")
offset_bin_breaks <- seq(-180, 180, by = 20)
offset_bin_labels <- paste(head(offset_bin_breaks, -1), tail(offset_bin_breaks, -1), sep = "-")
offset_bins <- cut(
  fb_data$fb_offset, breaks = offset_bin_breaks,
  include.lowest = TRUE, labels = offset_bin_labels
)

# Compute the median error per fb_offset bin
offset_median_boot_by_bin <- fb_data %>%
  mutate(offset_bin = offset_bins) %>%
  group_by(offset_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does error's median differ between noFB and FB conditions?
# Controlled for subjects
condition_median_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  median(samp$error[samp$condition == "FB"]) - median(samp$error[samp$condition == "noFB"])
}, R = R_boot)
condition_median_diff_ci <- boot.ci(condition_median_diff_boot, type = "perc")$percent[4:5]

# Does median error differ between mirrored positive/negative offset bins on average?
# Controlled for subjects
n_offset_bins <- length(offset_bin_labels)
offset_data <- fb_data %>% mutate(offset_bin = offset_bins)
offset_mirror_pos_bins <- offset_bin_labels[(n_offset_bins / 2 + 1):n_offset_bins]
offset_mirror_neg_bins <- rev(offset_bin_labels[1:(n_offset_bins / 2)])
offset_mirror_median_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ offset_data %>% filter(subj == .x))
  mean(map2_dbl(offset_mirror_pos_bins, offset_mirror_neg_bins, ~ {
    median(samp$error[samp$offset_bin == .x]) - median(samp$error[samp$offset_bin == .y])
  }))
}, R = R_boot)
offset_mirror_median_diff_ci <- boot.ci(offset_mirror_median_diff_boot, type = "perc")$percent[4:5]
```

```{r}
#| label: fig-error-by-condition-offset
#| fig-cap: "**Median error by condition and by visual feedback offset**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 10
#| fig-height: 6

# Define the plot for error vs. condition
plot_C <- ggplot(condition_median_boot, aes(x = condition, y = median, color = condition)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(labels = c(noFB = "No Feedback", FB = "Feedback")) +
  scale_color_brewer(palette = "Dark2", guide = "none") +
  theme_bw() +
  labs(x = "Condition", y = "Median(error) with 95% bootstrap CI")

# Always show the two bins nearest zero, alternate ticks outward from there
offset_bin_center_idx <- n_offset_bins / 2
left_ticks <- rev(seq(offset_bin_center_idx, 1, by = -2))
right_ticks <- seq(offset_bin_center_idx + 1, n_offset_bins, by = 2)
offset_bin_ticks <- offset_bin_labels[c(left_ticks, right_ticks)]

# Define the plot for error vs. fb_offset
plot_D <- ggplot(offset_median_boot_by_bin, aes(x = offset_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = offset_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Visual feedback offset", y = "Median(error) with 95% bootstrap CI")

(plot_C | plot_D) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Median error was higher in trials where visual feedback was provided (bootstrapped 95% CI of difference between two conditions = [`r round(condition_median_diff_ci[1], 2)`, `r round(condition_median_diff_ci[2], 2)`]$^\circ$), consistent with varying reliability of the visual feedback (@fig-error-by-condition-offset(a)). The above deviation from the forced fusion model based on a normative Bayesian observer has been shown before where the observers have a tendency to overweight signals from a sensory modality (vision) which can provide better information than their own proprioceptive sense [@Noppeney_2021].
- Median error is low for reliable visual feedback (low offsets), increases rapidly for positive offsets till around 60$^\circ$ and decreases thereafter (@fig-error-by-condition-offset(b)). On the other hand, median error increases gradually for negative offsets, plateaus around 60$^\circ$, then increases again (@fig-error-by-condition-offset(b)). Thus, participants' responses may be affected by the direction of the feedback offset (mirrored positive vs. negative bins, bootstrapped 95% CI of difference = [`r round(offset_mirror_median_diff_ci[1], 2)`, `r round(offset_mirror_median_diff_ci[2], 2)`]$^\circ$) along with its reliability. The extent of integration between proprioception and vision depends on the size of the conflict between the information from both sources [@Noppeney_2021].

```{r}
#| code-summary: ""
#| code-fold: true

# Does the variance of error grow across target bins?
# Controlling for individual subjects
error_sd_boot_by_bin <- data %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does error's SD differ between noFB and FB conditions?
# Controlled for subjects
condition_sd_boot <- data %>%
  group_by(condition) %>%
  group_modify(~ {
    group_data <- .x
    group_subjs <- unique(group_data$subj)
    b <- boot(group_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ group_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does error's SD grow with fb_offset?
# Controlled for subjects
offset_sd_boot_by_bin <- fb_data %>%
  mutate(offset_bin = offset_bins) %>%
  group_by(offset_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does error's SD differ between noFB and FB conditions? (magnitude of the difference)
# Controlled for subjects
condition_sd_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  sd(samp$error[samp$condition == "FB"]) - sd(samp$error[samp$condition == "noFB"])
}, R = R_boot)
condition_sd_diff_ci <- boot.ci(condition_sd_diff_boot, type = "perc")$percent[4:5]

# Does error's SD differ between mirrored positive/negative offset bins on average?
# Controlled for subjects
offset_mirror_sd_diff_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ offset_data %>% filter(subj == .x))
  mean(map2_dbl(offset_mirror_pos_bins, offset_mirror_neg_bins, ~ {
    sd(samp$error[samp$offset_bin == .x]) - sd(samp$error[samp$offset_bin == .y])
  }))
}, R = R_boot)
offset_mirror_sd_diff_ci <- boot.ci(offset_mirror_sd_diff_boot, type = "perc")$percent[4:5]

# Does |error| (1/accuracy) change with viewAmount (attention paid to the feedback cue)?
# FB trials only; controlled for subjects
accuracy_view_amount_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ fb_data %>% filter(subj == .x))
  coef(rq(abs(error) ~ viewAmount, tau = 0.5, data = samp))["viewAmount"]
}, R = R_boot)
accuracy_view_amount_slope_ci <- boot.ci(accuracy_view_amount_slope_boot, type = "perc")$percent[4:5]
```

```{r}
#| label: fig-error-variance
#| fig-cap: "**SD of error across target heading bins, condition, and visual feedback offset**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 12
#| fig-height: 5

# Define the plot for error's SD vs. target
plot_E <- ggplot(error_sd_boot_by_bin, aes(x = target_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Target Heading", y = "SD(error) with 95% bootstrap CI")

# Define the plot for error's SD vs. condition
plot_F <- ggplot(condition_sd_boot, aes(x = condition, y = sd, color = condition)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(labels = c(noFB = "No Feedback", FB = "Feedback")) +
  scale_color_brewer(palette = "Dark2", guide = "none") +
  theme_bw() +
  labs(x = "Condition", y = "SD(error) with 95% bootstrap CI")

# Define the plot for error's SD vs. fb_offset
plot_G <- ggplot(offset_sd_boot_by_bin, aes(x = offset_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = offset_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Visual feedback offset", y = "SD(error) with 95% bootstrap CI")

(plot_E | plot_F | plot_G) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Standard deviation (SD) of error may be a measure of uncertainty about the information. As @fig-error-variance(a) shows, SD of error grows with task difficulty, but it rises in two phases separated by a plateau in the range of 120$^\circ$ to 240$^\circ$.
- The amount of uncertainty was higher in trials where visual feedback was provided (bootstrapped 95% CI of difference = [`r round(condition_sd_diff_ci[1], 2)`, `r round(condition_sd_diff_ci[2], 2)`]$^\circ$) (@fig-error-variance(b)).
- The amount of uncertainty rises with unreliability of the visual feedback but plateaus around 60$^\circ$ for both positive and negative offsets (@fig-error-variance(c)). The uncertainty might be tracking the reliability of the visual feedback reinforcing the impact of conflict size on integration of visual and proprioceptive information. The uncertainty is higher for negative feedback offsets as compared to the corresponding positive offsets (mirrored positive vs. negative bins, bootstrapped 95% CI of difference = [`r round(offset_mirror_sd_diff_ci[1], 2)`, `r round(offset_mirror_sd_diff_ci[2], 2)`]$^\circ$).

```{r}
#| code-summary: ""
#| code-fold: true

# Define the trial_duration decile bins for plotting purposes
duration_bin_breaks <- quantile(data$trial_duration, probs = seq(0, 1, by = 0.1))
# Label bins in seconds for readability; computation stays in msec
duration_bin_labels <- paste(head(round(duration_bin_breaks / 1000, 1), -1), tail(round(duration_bin_breaks / 1000, 1), -1), sep = "-")
duration_bins <- cut(
  data$trial_duration, breaks = duration_bin_breaks,
  include.lowest = TRUE, labels = duration_bin_labels
)

# Compute the median of error per trial_duration bin
error_median_boot_by_duration <- data %>%
  mutate(duration_bin = duration_bins) %>%
  group_by(duration_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Compute the SD of error per trial_duration bin
error_sd_boot_by_duration <- data %>%
  mutate(duration_bin = duration_bins) %>%
  group_by(duration_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does error's median grow with trial_duration?
# Controlled for subjects
duration_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  coef(rq(error ~ trial_duration, tau = 0.5, data = samp))["trial_duration"]
}, R = R_boot)
duration_slope_ci <- boot.ci(duration_slope_boot, type = "perc")$percent[4:5]
```

```{r}
#| label: fig-error-by-trial-duration
#| fig-cap: "**Median and SD of error across trial duration deciles**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 10
#| fig-height: 6

# Build the plot for median error vs. trial_duration
plot_error_by_duration <- ggplot(error_median_boot_by_duration, aes(x = duration_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "trial duration (sec)", y = "Median(error) with 95% bootstrap CI")

# Build the plot for error's SD vs. trial_duration
plot_error_sd_by_duration <- ggplot(error_sd_boot_by_duration, aes(x = duration_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "trial duration (sec)", y = "SD(error) with 95% bootstrap CI")

(plot_error_by_duration | plot_error_sd_by_duration) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Median error increases slightly with trial duration (bootstrapped 95% CI for median regression slope [`r format(round(duration_slope_ci[1], 4), scientific = FALSE)`, `r format(round(duration_slope_ci[2], 4), scientific = FALSE)`]$^\circ$/msec) (@fig-error-by-trial-duration(a)), and so does the uncertainty (@fig-error-by-trial-duration(b)).

```{r}
#| code-summary: ""
#| code-fold: true

# Define the fb_time decile bins for plotting purposes, FB trials only
fb_time_bin_breaks <- quantile(fb_data$fb_time, probs = seq(0, 1, by = 0.1))
# Label bins in seconds for readability; computation stays in msec
fb_time_bin_labels <- paste(head(round(fb_time_bin_breaks / 1000, 1), -1), tail(round(fb_time_bin_breaks / 1000, 1), -1), sep = "-")
fb_time_bins <- cut(
  fb_data$fb_time, breaks = fb_time_bin_breaks,
  include.lowest = TRUE, labels = fb_time_bin_labels
)

# Compute the median of error per fb_time bin
error_median_boot_by_fb_time <- fb_data %>%
  mutate(fb_time_bin = fb_time_bins) %>%
  group_by(fb_time_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Compute the SD of error per fb_time bin
error_sd_boot_by_fb_time <- fb_data %>%
  mutate(fb_time_bin = fb_time_bins) %>%
  group_by(fb_time_bin) %>%
  # Stratify by participants
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$error)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does error's median grow with fb_time?
fb_time_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ fb_data %>% filter(subj == .x))
  coef(rq(error ~ fb_time, tau = 0.5, data = samp))["fb_time"]
}, R = R_boot)
fb_time_slope_ci <- boot.ci(fb_time_slope_boot, type = "perc")$percent[4:5]
```

```{r}
#| label: fig-error-by-fb-time
#| fig-cap: "**Median and SD of error across different times (deciles) at which the feedback was displayed**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 10
#| fig-height: 6

# Build the plot for median error vs. fb_time
plot_error_by_fb_time <- ggplot(error_median_boot_by_fb_time, aes(x = fb_time_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "feedback display time (sec)", y = "Median(error) with 95% bootstrap CI")

# Build the plot for error's SD vs. fb_time
plot_error_sd_by_fb_time <- ggplot(error_sd_boot_by_fb_time, aes(x = fb_time_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "feedback display time (sec)", y = "SD(error) with 95% bootstrap CI")

(plot_error_by_fb_time | plot_error_sd_by_fb_time) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Median error does not depend on when the feedback was displayed (bootstrapped 95% CI for median regression slope [`r format(round(fb_time_slope_ci[1], 4), scientific = FALSE)`, `r format(round(fb_time_slope_ci[2], 4), scientific = FALSE)`]$^\circ$/msec) (@fig-error-by-fb-time(a)), but the uncertainty is less when the feedback is displayed earlier rather than later (@fig-error-by-fb-time(b)).

From the above characteristics of the participants' responses, it is clear that the magnitude of error depends on both the proprioceptive and visual information. The final perceptual estimate is computed by averaging the individual estimates weighted by their reliabilities [@Noppeney_2021], but this may or may not happen in a normative manner depending on the size of the conflict between the two information sources. The uncertainty depends on task difficulty (`target`), trial duration, presence or absence of visual feedback, reliability of the visual feedback (`|fb_offset|`), direction of the offset, and the time when the feedback was displayed.  

Accuracy (1/`|error|`) improves as attention increases (`viewAmount` decreases) (bootstrapped 95% CI for the median regression slope [`r round(accuracy_view_amount_slope_ci[1], 3)`, `r round(accuracy_view_amount_slope_ci[2], 3)`]). A good model should have the same behavioral feature.

### Subjective Confidence Tracks Performance Accuracy

```{r}
#| code-summary: ""
#| code-fold: true

# Compute the median of conf per target bins
conf_median_boot_by_bin <- data %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      median(samp$conf)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(median = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does subjective confidence (conf) grow with target (task difficulty)?
# Controlled for subjects
conf_target_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  coef(rq(conf ~ target, tau = 0.5, data = samp))["target"]
}, R = R_boot)
conf_target_slope_ci <- boot.ci(conf_target_slope_boot, type = "perc")$percent[4:5]

# Does conf's SD also grow with target?
# Controlling for individual subjects
conf_sd_boot_by_bin <- data %>%
  mutate(target_bin = target_bins) %>%
  group_by(target_bin) %>%
  group_modify(~ {
    bin_data <- .x
    bin_subjs <- unique(bin_data$subj)
    b <- boot(bin_subjs, function(d, i) {
      samp <- map_dfr(d[i], ~ bin_data %>% filter(subj == .x))
      sd(samp$conf)
    }, R = R_boot)
    ci <- boot.ci(b, type = "perc")$percent[4:5]
    tibble(sd = b$t0, ci_low = ci[1], ci_high = ci[2])
  })

# Does conf track |error| ie. 1/accuracy?
# Controlled for subjects
conf_error_slope_boot <- boot(subjs, function(d, i) {
  samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
  coef(rq(conf ~ abs(error), tau = 0.5, data = samp))["abs(error)"]
}, R = R_boot)
conf_error_slope_ci <- boot.ci(conf_error_slope_boot, type = "perc")$percent[4:5]
```

```{r}
#| label: fig-conf-by-target
#| fig-cap: "**Median and SD of subjective confidence across target heading bins**"
#| code-summary: ""
#| code-fold: true
#| fig-width: 10
#| fig-height: 6

# Define the plot for conf vs. target
plot_H <- ggplot(conf_median_boot_by_bin, aes(x = target_bin, y = median)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Target Heading", y = "Median(conf) with 95% bootstrap CI")

# Define the plot for conf's SD vs. target
plot_I <- ggplot(conf_sd_boot_by_bin, aes(x = target_bin, y = sd)) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high)) +
  scale_x_discrete(breaks = target_bin_ticks) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  labs(x = "Target Heading", y = "SD(conf) with 95% bootstrap CI")

(plot_H | plot_I) + plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

- Subjective confidence reduces with task difficulty (bootstrapped 95% CI for the median regression slope [`r round(conf_target_slope_ci[1], 3)`, `r round(conf_target_slope_ci[2], 3)`]) similar to error which is an objective measure of performance (@fig-conf-by-target(a)).
- But SD of this subjective measure does not grow with task difficulty (@fig-conf-by-target(b)).
- Confidence tracks performance accuracy (1/`|error|`) (bootstrapped 95% CI for the median regression slope [`r round(conf_error_slope_ci[1], 3)`, `r round(conf_error_slope_ci[2], 3)`]).

Thus, participants track their performance based on the task's difficulty and how well they actually did. A good model should have the same behavioral feature.

## Models

Generalized Additive Models for Location Scale and Shape (`gamlss` library in R) [@R.A.Rigby_2005] were chosen for modelling error since it allows modelling not only of the central tendency, but also of the other parameters of the distribution like the standard deviation. GAMLSS uses penalized maximum likelihood estimatation (MLE) to fit models. A distribution family for the predicted variable can be selected from a very general family of distributions. A skew-t (`SST`) family fit the error distribution far better than a normal distribution (see @sec-appendix). The same family was used for the following models. The shape parameters (skewness, $\nu$ and kurtosis, $\tau$) were not modelled since the overall shape of the uncertainty is usually unique to each individual and may not change in the time period of the experiment. Every model controls for inter-participant variability by including the participants as random effects predictor. Penalized smooth functions were used for the predictors which require no assumption of the order of relationship and penalize overfitting due to noise.

### Naive Unisensory Model

This model naively assumes that error depends only on the proprioceptive signal available from target and amount of time it takes to respond.

$$
\begin{aligned}
\text{error} &\sim SST(\mu, \sigma, \nu, \tau) \\
\mu &= f_1(\text{target}) + f_2(\text{trial\_duration}) + b_{subj} \\
\log(\sigma) &= f_3(\text{target}) + f_4(\text{trial\_duration}) + b_{subj}
\end{aligned}
$$

where each $f_i$ is a penalized smooth function and $b_{subj}$ is a random intercept for per-subject fit. No collinearity existed between the chosen predictors (@fig-unisensory(b)).

```{r}
#| code-summary: Fit unisensory model
#| code-fold: true
#| message: false

# Unisensory formulas
unisensory_data <- data
unisensory_mu_formula <- error ~ pbc(target) + pb(trial_duration) + re(random = ~1|subj, level = 0)
unisensory_sigma_formula <- ~ pbc(target) + pb(trial_duration) + re(random = ~1|subj, level = 0)
# Fit the model
unisensory_fit <- gamlss(
  formula = unisensory_mu_formula,
  sigma.formula = unisensory_sigma_formula,
  family = SST(),
  data = unisensory_data,
  method = mixed(20, 100),
  control = gamlss.control(n.cyc = 300, trace = FALSE)
)

# Tidy labels for the collinearity predictors
unisensory_term_labels <- c(target = "Target Heading", trial_duration = "Trial Duration", subj = "Participant")

# Check collinearity between the predictors, controlling for subj
unisensory_vif <- car::vif(lm(error ~ target + trial_duration + subj, data = data))
# Keep only the adjusted GVIF column
unisensory_vif_table <- unisensory_vif[, "GVIF^(1/(2*Df))", drop = FALSE] %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  mutate(term = unisensory_term_labels[term]) %>%
  rename(Term = term, `Adjusted GVIF` = `GVIF^(1/(2*Df))`) %>%
  mutate(`Adjusted GVIF` = round(`Adjusted GVIF`, 2))

# 10th/30th/50th/70th/90th percentile trial_duration, one predicted SD curve each
duration_levels <- quantile(data$trial_duration, probs = c(0.1, 0.3, 0.5, 0.7, 0.9))

# Grid spanning target, one row per duration level
unisensory_grid <- expand_grid(
  target = seq(min(data$target), max(data$target), length.out = 100),
  trial_duration = duration_levels,
  subj = factor("population")
)
unisensory_grid$pred_sigma <- predictAll(
  unisensory_fit, newdata = unisensory_grid, type = "response", data = unisensory_data, output = "list"
)$sigma
```

```{r}
#| label: fig-unisensory
#| fig-cap: "**Naive Unisensory model**: (a) predicted uncertainty against target at 5 trial durations; (b) predictor collinearity"
#| fig-width: 10
#| fig-height: 6
#| code-summary: Plot unisensory model
#| code-fold: true
#| message: false

# Plot predicted SD vs. target, one line per trial_duration level
unisensory_sd_plot <- unisensory_grid %>%
  mutate(trial_duration = factor(round(trial_duration / 1000, 1), levels = round(duration_levels / 1000, 1))) %>%
  ggplot(aes(x = target, y = pred_sigma, color = trial_duration)) +
  geom_line() +
  scale_color_viridis_d(direction = -1) +
  labs(x = "Target Heading", y = "Predicted SD of error", color = "Trial Duration (sec)") +
  theme_bw() +
  theme(axis.title = element_text(size = 16), axis.text = element_text(size = 12))

(unisensory_sd_plot | wrap_table(unisensory_vif_table %>% dark_header_gt(), panel = "full")) +
  plot_layout(widths = c(0.5, 0.5)) +
  plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

Predicted uncertainty from this model does not increase monotonically with target heading (@fig-unisensory(a)), unlike the behavioral relationship between error and target (@fig-error-variance(a)).

### Cue Combination Model

A visual only model which assumes that error depends only on the visual signal available from target and the visual feedback's reliability was built first.

$$
\begin{aligned}
\text{error} &\sim SST(\mu, \sigma, \nu, \tau) \\
\mu &= f_1(\text{target}) + f_2(\text{fb\_offset}) + b_{subj} \\
\log(\sigma) &= f_3(\text{target}) + f_4(\text{fb\_offset}) + b_{subj}
\end{aligned}
$$

The cue combination model combines the unisensory and visual only models' predictions by weighting them according to their precisions [@Noppeney_2021] using the formula (assumes predicted error is Gaussian-like)[@Kording_2007]:

$$
\hat{\mu}_{combined} = \frac{\mu_{uni}/\sigma_{uni}^2 + \mu_{vis}/\sigma_{vis}^2}{1/\sigma_{uni}^2 + 1/\sigma_{vis}^2}
$$

```{r}
#| code-summary: Fit cue combination model
#| code-fold: true
#| message: false
#| warning: false

# Visual-only formulas
visual_only_data <- fb_data
visual_only_mu_formula <- error ~ pbc(target) + pb(fb_offset) + re(random = ~1|subj, level = 0)
visual_only_sigma_formula <- ~ pbc(target) + pb(fb_offset) + re(random = ~1|subj, level = 0)
# Fit the model
visual_only_fit <- gamlss(
  formula = visual_only_mu_formula,
  sigma.formula = visual_only_sigma_formula,
  family = SST(),
  data = visual_only_data,
  method = mixed(20, 100),
  control = gamlss.control(n.cyc = 300, trace = FALSE)
)

# Tidy labels for the collinearity predictors
visual_only_term_labels <- c(target = "Target Heading", fb_offset = "Feedback Offset", subj = "Participant")

# Check collinearity between the predictors, controlling for subj
visual_only_vif <- car::vif(lm(error ~ target + fb_offset + subj, data = fb_data))
# Keep only the adjusted GVIF column
visual_only_vif_table <- visual_only_vif[, "GVIF^(1/(2*Df))", drop = FALSE] %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  mutate(term = visual_only_term_labels[term]) %>%
  rename(Term = term, `Adjusted GVIF` = `GVIF^(1/(2*Df))`) %>%
  mutate(`Adjusted GVIF` = round(`Adjusted GVIF`, 2))

# 5 evenly-spaced target levels for hue, 5 trial_duration quantile levels for faceting
target_levels <- c(20, 80, 140, 200, 260)
cue_duration_levels <- quantile(fb_data$trial_duration, probs = c(0.1, 0.3, 0.5, 0.7, 0.9))

# Grid spanning fb_offset, one row per target x trial_duration combination
cue_combination_grid <- expand_grid(
  fb_offset = seq(min(fb_data$fb_offset), max(fb_data$fb_offset), length.out = 100),
  target = target_levels,
  trial_duration = cue_duration_levels,
  subj = factor("population")
)

# Unisensory and visual-only predictions on the grid
cue_uni_pred <- predictAll(
  unisensory_fit, newdata = cue_combination_grid, type = "response", data = unisensory_data, output = "list"
)
cue_vis_pred <- predictAll(
  visual_only_fit, newdata = cue_combination_grid, type = "response", data = visual_only_data, output = "list"
)

# Precision-weighted combined SD
cue_combination_grid$pred_sigma <- sqrt(1 / (1 / cue_uni_pred$sigma^2 + 1 / cue_vis_pred$sigma^2))
```

```{r}
#| label: fig-cue-combination
#| fig-cap: "**Cue Combination model**: (a) combined predicted estimate against feedback offset, by target, faceted by trial duration; (b) predictor collinearity"
#| fig-width: 12
#| fig-height: 6
#| code-summary: Plot cue combination model
#| code-fold: true
#| message: false
#| warning: false

# Plot combined predicted SD vs. fb_offset, colored by target, faceted by trial_duration
cue_combination_plot <- cue_combination_grid %>%
  mutate(
    target = factor(round(target), levels = round(target_levels)),
    trial_duration = factor(paste0(round(trial_duration / 1000, 1), " sec"), levels = paste0(round(cue_duration_levels / 1000, 1), " sec"))
  ) %>%
  ggplot(aes(x = fb_offset, y = pred_sigma, color = target)) +
  geom_line() +
  facet_wrap(~trial_duration) +
  scale_color_viridis_d(direction = -1) +
  labs(x = "Feedback Offset", y = "Predicted SD of error", color = "Target Heading") +
  theme_bw() +
  theme(axis.title = element_text(size = 16), axis.text = element_text(size = 12))

(wrap_elements(full = reposition_legend(cue_combination_plot, "center", panel = "panel-3-2", plot = FALSE)) |
  wrap_table(visual_only_vif_table %>% dark_header_gt(size = 30), panel = "full")) +
  plot_layout(widths = c(0.55, 0.45)) +
  plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

The predicted uncertainty of this model was low for reliable visual feedback and increased as offset increased until around 50$\circ$. Negative offsets showed higher predicted uncertainty as compared to positive offsets (@fig-cue-combination(a)). Both of these features are consistent with the behavioral relationship seen between error and reliability (@fig-error-variance(c)). Predicted uncertainty increased with both task difficulty and amount of time taken to respond (@fig-cue-combination(a)), consistent with the behavioral relationship between these variables (@fig-error-variance(a), @fig-error-by-trial-duration(b)). No collinearity existed between the chosen predictors (@fig-cue-combination(b)).

### Flexible Multisensory Model

This model makes no assumptions about the distribution of the predicted error or how the proprioceptive and visual signals are combined. A high-dimensional feature space is constructed from target, feedback reliability, amount of time spent to respond, the amount of visual information received (`viewAmount`). Interaction terms are included where coefficients for one variable (for example target representing proprioception) are allowed to change smoothly with the value of another variable (for example feedback offset representing vision) [@Hastie_1993]. Thus, the direction and magnitude of feedback offset acts as an effect modifier for target. This may resemble how integration of information takes place at the neuronal level via dendritic modulation of activity. The reparameterised skew-t family (`SST()`) selected was especially useful for defining these formulas since the SD of the prediction is represented by $\sigma$ alone, unlike other skewed distributions (for example skew-normal) which compute SD of predictions using $\sigma$ and $\nu$ parameters.

$$
\begin{aligned}
\text{error} &\sim SST(\mu, \sigma, \nu, \tau) \\
\mu &= f_1(\text{target}) + f_2(\text{trial\_duration}) + f_3(\text{fb\_offset}) + f_4(\text{viewAmount}) \\
    &\quad + g_1(\text{target}, \text{fb\_offset}) + g_2(\text{trial\_duration}, \text{fb\_offset}) + g_3(\text{viewAmount}, \text{fb\_offset}) + b_{subj} \\
\log(\sigma) &= \text{(same structure as } \mu\text{)}
\end{aligned}
$$

where each $g_i$ is a varying-coefficient smooth function for interactions between variables and their effect modifiers.

```{r}
#| code-summary: Fit multisensory model
#| code-fold: true
#| message: false
#| warning: false

# Multisensory formulas
multisensory_data <- fb_data
multisensory_mu_formula <- error ~ pbc(target) + pb(trial_duration) + pb(fb_offset) + pb(viewAmount) +
                                    pvc(target, by = fb_offset) +
                                    pvc(trial_duration, by = fb_offset) +
                                    pvc(viewAmount, by = fb_offset) +
                                    re(random = ~1|subj, level = 0)
multisensory_sigma_formula <- ~ pbc(target) + pb(trial_duration) + pb(fb_offset) + pb(viewAmount) +
                                pvc(target, by = fb_offset) +
                                pvc(trial_duration, by = fb_offset) +
                                pvc(viewAmount, by = fb_offset) +
                                re(random = ~1|subj, level = 0)
# Fit the model
multisensory_fit <- gamlss(
  formula = multisensory_mu_formula,
  sigma.formula = multisensory_sigma_formula,
  family = SST(),
  data = multisensory_data,
  method = mixed(20, 100),
  control = gamlss.control(n.cyc = 300, trace = FALSE)
)

# Tidy labels for the collinearity predictors
multisensory_term_labels <- c(
  target = "Target Heading", trial_duration = "Trial Duration",
  fb_offset = "Feedback Offset", viewAmount = "View Amount", subj = "Participant"
)

# Check collinearity between the predictors and their interactions with fb_offset, controlling for subj
multisensory_vif <- car::vif(
  lm(error ~ (target + trial_duration + viewAmount) * fb_offset + subj, data = fb_data),
  type = "predictor"
)
# Keep only the adjusted GVIF column
multisensory_vif_table <- multisensory_vif[, "GVIF^(1/(2*Df))", drop = FALSE] %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  mutate(term = multisensory_term_labels[term]) %>%
  rename(Term = term, `Adjusted GVIF` = `GVIF^(1/(2*Df))`) %>%
  mutate(`Adjusted GVIF` = round(`Adjusted GVIF`, 2))

# 5 trial_duration quantile levels for faceting, viewAmount fixed at median
multisensory_duration_levels <- quantile(fb_data$trial_duration, probs = c(0.1, 0.3, 0.5, 0.7, 0.9))
multisensory_median_view_amount <- median(fb_data$viewAmount)

# Grid spanning fb_offset, one row per target x trial_duration combination
multisensory_grid <- expand_grid(
  fb_offset = seq(min(fb_data$fb_offset), max(fb_data$fb_offset), length.out = 100),
  target = target_levels,
  trial_duration = multisensory_duration_levels,
  viewAmount = multisensory_median_view_amount,
  subj = factor("population")
)
multisensory_grid$pred_sigma <- predictAll(
  multisensory_fit, newdata = multisensory_grid, type = "response", data = multisensory_data, output = "list"
)$sigma
```

```{r}
#| label: fig-multisensory
#| fig-cap: "**Flexible Multisensory model**: (a) predicted estimate against feedback offset, by target, faceted by trial duration, at median view amount; (b) predictor collinearity"
#| fig-width: 12
#| fig-height: 6
#| code-summary: Plot multisensory model
#| code-fold: true
#| message: false
#| warning: false

# Plot predicted SD vs. fb_offset, colored by target, faceted by trial_duration
multisensory_plot <- multisensory_grid %>%
  mutate(
    target = factor(round(target), levels = round(target_levels)),
    trial_duration = factor(
      paste0(round(trial_duration / 1000, 1), " sec"), levels = paste0(round(multisensory_duration_levels / 1000, 1), " sec")
    )
  ) %>%
  ggplot(aes(x = fb_offset, y = pred_sigma, color = target)) +
  geom_line() +
  facet_wrap(~trial_duration) +
  scale_color_viridis_d(direction = -1) +
  labs(x = "Feedback Offset", y = "Predicted SD of error", color = "Target Heading") +
  theme_bw() +
  theme(axis.title = element_text(size = 16), axis.text = element_text(size = 12))

(wrap_elements(full = reposition_legend(multisensory_plot, "center", panel = "panel-3-2", plot = FALSE)) |
  wrap_table(multisensory_vif_table %>% dark_header_gt(size = 30), panel = "full")) +
  plot_layout(widths = c(0.55, 0.45)) +
  plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

The predicted uncertainty of this model behaves similarly to the cue combination model (@fig-multisensory(a)). The predicted uncertainty for target heading of 20$\circ$ increases as trial duration increases. But this increase is asymmetric for corresponding negative and positive offsets. The model may be capturing an interaction between low target values, higher trial durations and positive offsets. For example, a positive offset for a smaller turn pushes the error in the same direction, especially when more time was taken to respond. Such an effect was not captured by the cue combination model. Another possible explanation is a sparsity of training data at the confluence of low target values and high trial durations making the predictions less stable. No collinearity existed between the chosen predictors (@fig-multisensory(b)).

## Model Comparison

```{r}
#| label: fig-model-comparison
#| fig-cap: "(a) Training BIC; (b) 5-fold CV RMSE across all models"
#| fig-width: 10
#| fig-height: 2
#| code-summary: ""
#| code-fold: true
#| message: false

# BIC for the two likelihood-based models
model_comparison_bic <- tibble(
  Model = c("Naive Unisensory", "Flexible Multisensory"),
  BIC = c(
    round(AIC(unisensory_fit, k = log(nobs(unisensory_fit)))),
    round(AIC(multisensory_fit, k = log(nobs(multisensory_fit))))
  )
) %>%
  arrange(BIC) %>%
  dark_header_gt()

# Raw per-fold RMSE from scripts/model-cv.R, computed offline overnight
cv_results <- readRDS(here("data", "cv-results.rds"))

# Mean +/- 2SE RMSE per model across converged folds, smooth dropped
cv_summary <- cv_results %>%
  filter(model != "smooth") %>%
  group_by(model) %>%
  summarise(
    mean_rmse = mean(rmse, na.rm = TRUE),
    se_rmse = sd(rmse, na.rm = TRUE) / sqrt(sum(!is.na(rmse))),
    .groups = "drop"
  ) %>%
  arrange(mean_rmse) %>%
  mutate(
    model = factor(model,
      levels = c("unisensory", "classical", "multisensory"),
      labels = c("Naive Unisensory", "Cue Combination", "Flexible Multisensory")
    ),
    rmse = sprintf("%.1f ± %.1f", mean_rmse, 2 * se_rmse)
  ) %>%
  dplyr::select(model, rmse) %>%
  rename(Model = model, `RMSE (mean ± 2SE)` = rmse) %>%
  dark_header_gt()

(wrap_table(model_comparison_bic, panel = "full") | wrap_table(cv_summary, panel = "full")) +
  plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

The Bayesian Information Criterion (BIC) score (penalizes complexity) was much lower for the flexible multisensory model than the naive unisensory model (@fig-model-comparison(a)). A 5-fold cross validation of all 3 models showed the same ordering by average RMSE: naive unisensory, then cue combination, then flexible multisensory (@fig-model-comparison(b)).

## Behavioral Validation

```{r}
#| code-summary: ""
#| code-fold: true
#| message: false

# Unisensory predicted on the full data
uni_pred_full <- predictAll(unisensory_fit, newdata = data, type = "response", data = unisensory_data, output = "list")
target_error_data <- data %>%
  mutate(unisensory_sd = uni_pred_full$sigma)

# Unisensory, visual-only and multisensory predicted on FB trials
uni_pred_fb <- predictAll(unisensory_fit, newdata = fb_data, type = "response", data = unisensory_data, output = "list")
vis_pred <- predictAll(visual_only_fit, newdata = fb_data, type = "response", data = visual_only_data, output = "list")
multi_pred <- predictAll(multisensory_fit, newdata = fb_data, type = "response", data = multisensory_data, output = "list")
view_amount_data <- fb_data %>%
  mutate(
    unisensory_abs_error = abs(uni_pred_fb$mu),
    cue_combination_abs_error = abs((uni_pred_fb$mu / uni_pred_fb$sigma^2 + vis_pred$mu / vis_pred$sigma^2) / (1 / uni_pred_fb$sigma^2 + 1 / vis_pred$sigma^2)),
    multisensory_abs_error = abs(multi_pred$mu)
  )

# Cue combination and multisensory predicted SD, joined onto target_error_data by subj and trial
target_error_data <- target_error_data %>%
  left_join(
    fb_data %>%
      mutate(
        cue_combination_sd = sqrt(1 / (1 / uni_pred_fb$sigma^2 + 1 / vis_pred$sigma^2)),
        multisensory_sd = multi_pred$sigma
      ) %>%
      dplyr::select(subj, trial, cue_combination_sd, multisensory_sd),
    by = c("subj", "trial")
  )

# Bootstrapped median regression slope of sd_col against a single predictor, controlling for subj
validation_slope <- function(sd_col, predictor, data) {
  b <- boot(subjs, function(d, i) {
    samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
    coef(rq(reformulate(predictor, response = sd_col), tau = 0.5, data = samp))[[2]]
  }, R = R_boot)
  boot.ci(b, type = "perc")$percent[4:5]
}

# Bootstrapped median regression slope of abs_error_col ~ viewAmount, controlling for subj
validation_view_amount_slope <- function(abs_error_col, data) {
  b <- boot(subjs, function(d, i) {
    samp <- map_dfr(d[i], ~ data %>% filter(subj == .x))
    coef(rq(reformulate("viewAmount", response = abs_error_col), tau = 0.5, data = samp))[[2]]
  }, R = R_boot)
  boot.ci(b, type = "perc")$percent[4:5]
}

# Format a [lo, hi] CI pair as a display string
format_ci <- function(ci) paste0("[", round(ci[1], 3), ", ", round(ci[2], 3), "]")

validation_models <- c("Naive Unisensory", "Cue Combination", "Flexible Multisensory")
validation_sd_cols <- c("unisensory_sd", "cue_combination_sd", "multisensory_sd")

# Slope of predicted SD against |error|, per model
target_error_table <- tibble(
  Model = validation_models,
  `Slope (predicted SD ~ |error|)` = map_chr(validation_sd_cols, ~ format_ci(validation_slope(.x, "abs(error)", target_error_data)))
)

# Slope of predicted |error| against viewAmount, Naive Unisensory and Cue Combination
view_amount_table <- tibble(
  Model = c("Naive Unisensory", "Cue Combination"),
  `Slope (predicted |error| ~ viewAmount)` = map_chr(
    c("unisensory_abs_error", "cue_combination_abs_error"),
    ~ format_ci(validation_view_amount_slope(.x, view_amount_data))
  )
)

# Multisensory predicted |error| across viewAmount (10th/median/90th percentile), by 6 feedback offset levels
multi_view_amount_grid <- expand_grid(
  target = median(fb_data$target),
  trial_duration = median(fb_data$trial_duration),
  fb_offset = c(-120, -60, -30, 30, 60, 120),
  viewAmount = quantile(fb_data$viewAmount, probs = c(0.1, 0.5, 0.9)),
  subj = factor("population")
)
multi_view_amount_grid$pred_abs_error <- abs(predictAll(
  multisensory_fit, newdata = multi_view_amount_grid, type = "response", data = multisensory_data, output = "list"
)$mu)
```

```{r}
#| label: fig-behavioral-validation
#| fig-cap: "(a) Flexible Multisensory predicted |error| against viewAmount, by feedback offset; (b) bootstrapped slopes: predicted SD ~ |error| (top), predicted |error| ~ viewAmount (bottom)"
#| fig-width: 13
#| fig-height: 6
#| code-summary: ""
#| code-fold: true
#| message: false

# Plot predicted |error| vs viewAmount, colored by feedback offset
multi_view_amount_plot <- multi_view_amount_grid %>%
  mutate(fb_offset = factor(fb_offset, levels = c(-120, -60, -30, 30, 60, 120))) %>%
  ggplot(aes(x = viewAmount, y = pred_abs_error, color = fb_offset)) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_color_brewer(palette = "RdBu") +
  labs(x = "View Amount", y = "Predicted |error|", color = "Feedback Offset") +
  theme_bw() +
  theme(axis.title = element_text(size = 16), axis.text = element_text(size = 12))

(multi_view_amount_plot | (
  wrap_table(target_error_table %>% dark_header_gt(), panel = "full") /
    wrap_table(view_amount_table %>% dark_header_gt(size = 18), panel = "full") +
    plot_layout(widths = c(0.50, 0.50))
)) +
  plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ')')
```

Predicted uncertainty for all three models tracks performance accuracy (@fig-behavioral-validation(b), top), in the same manner as the subjective confidence measure. But naive unisensory and cue combination models' predicted `|error|` decreases as attention increases (`viewAmount`) (@fig-behavioral-validation(b), bottom). The flexible multisensory model instead shows predicted `|error|` increasing with `viewAmount` across all six feedback offset levels (@fig-behavioral-validation(a)), consistent with the behavioral relationship of these variables.

In conclusion, the flexible multisensory model is behaviorally consistent and performs similarly to the cue combination model for integration between proprioception and vision. The cue combination model has been suggested as one of the mechanisms for the binding problem, but several suboptimalities have been indicated before [@Noppeney_2021], such as:

- Observers arbitrarily switch between segregation and integration at a fixed conflict size, without accounting for their sensory uncertainties.
- Integration deviated from normative fusion for small conflict sizes when the participants were asked to selectively attend and report their perception under one sensory modality. A complex interaction between multisensory processing and attention was attributed as one of the mechanisms for the deviation in this specific case.
- The experimenters reported that a hybrid model which combined path integration from proprioception signal and cue combination performed better than individual models [@Harootonian_2022].

The flexible multisensory model presented above uses a different approach grounded in effect modulation between features which could mirror the dendritic modulation seen at neuronal level. The high dimensional feature space limits the interpretability of the model. But the internal representational structure of the brain may be similar to this high dimensional feature space. The compact size and modular nature of electroencephalography (EEG) could be useful to design a similar experiment to elucidate this internal representational structure.

One thing is clear to me: the concepts and mechanisms of multisensory processing are applicable to spatial cognition questions and should be considered when investigating how the sense of space is built.

## Appendix {#sec-appendix}

```{r}
#| label: fig-appendix-family
#| fig-cap: "**Worm plots for Normal, Skew-Normal, Skew-t and Johnson's SU fits to raw error**"
#| fig-width: 10
#| fig-height: 8
#| code-summary: ""
#| code-fold: true
#| warning: false

# Fit all four families directly to error
error_data <- data
family_no <- gamlss(error ~ 1, family = NO(), data = error_data, trace = FALSE)
family_sn2 <- gamlss(error ~ 1, family = SN2(), data = error_data, trace = FALSE)
family_sst <- gamlss(error ~ 1, family = SST(), data = error_data, trace = FALSE)
family_jsu <- gamlss(error ~ 1, family = JSU(), data = error_data, trace = FALSE)

# Display the worm plots in a single 2x2 base graphics layout
# (base graphics, not ggplot, so patchwork does not apply here)
par(mfrow = c(2, 2))
wp(family_no, ylim.all = 0.3)
title(paste0("Normal, BIC = ", round(AIC(family_no, k = log(nobs(family_no))))))
wp(family_sn2, ylim.all = 0.3)
title(paste0("Skew-Normal, BIC = ", round(AIC(family_sn2, k = log(nobs(family_sn2))))))
wp(family_sst, ylim.all = 0.3)
title(paste0("Skew-t, BIC = ", round(AIC(family_sst, k = log(nobs(family_sst))))))
wp(family_jsu, ylim.all = 0.3)
title(paste0("Johnson's SU, BIC = ", round(AIC(family_jsu, k = log(nobs(family_jsu))))))
par(mfrow = c(1, 1))
```

## References